---
title: "analysis_EU_election"
author: "Dominik Bär"
date: "2025-01-30"
output: html_document
---
```{r}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# File description

```{r}

# This file contains the analysis of Meta ads on election outcomes

```

# Set up environment



```{r, include=FALSE, echo=FALSE}
install.packages("sf")
# Clean environment
rm(list = ls())

# Load packages
library(arrow)
library(tidyverse)
library(lubridate)
library(ggrepel)
library(MatchIt)
library(WeightIt)
library(cobalt)
library(marginaleffects)
library(lme4)
library(broom)
library(sandwich)
library(clubSandwich)
library(lmtest)
library(ggpattern)
library(transport)
library(furrr)
library(betareg)
library(ggeffects)
library(sf)
# Load helpers
source("utils.R")

# Set seed
set.seed(42)

# Define paths to data
path_data <- "../../Data/"
path_figures <- "../../Doc/Nat Hum Behav/figures/"

```

# Graph theme setup

```{r}

theme_set(
  theme_bw() +
    theme(legend.position = c(0.7, 0.9),
          legend.title = element_blank(), 
          legend.direction = "horizontal",
          legend.text = element_text(colour="black", size=12), 
          legend.background=element_rect(fill="transparent", colour=NA),
          legend.key = element_rect(fill = "transparent", colour = "transparent"),
          legend.key.width = unit(0.5, "cm"), 
          legend.key.height = unit(0.5, "cm")
    ) + 
    theme(axis.text.x=element_text(colour = "black", size=12, vjust=0.5), 
          axis.text.y=element_text(colour = "black", size=12, vjust=0.5),
          axis.title.x=element_text(size=12), 
          axis.title.y=element_text(size=12, vjust=1.5)
    ) #+
    #theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
)

# Color mappings
extremist_colors <- c("darkred", "darkgreen", "darkblue")
populist_colors <- c("darkcyan", "darkorange")

```

## Inverse probability weighting

```{r}

perform_ipw <- function(data, balancing_vars, treatment_var, outcome_var){
  
  # Handle missing values
  data <- data %>%
    filter(complete.cases(select(., all_of(balancing_vars), all_of(treatment_var), all_of(outcome_var))))
  
  # Check number of populist and non-populist ads
  data %>%
    group_by(!!sym(treatment_var)) %>%
    summarize(n_ads = n())
  
  # Raise error if there are no (non)populist ads
  if(nrow(filter(data, !!sym(treatment_var) == 0)) == 0 | nrow(filter(data, !!sym(treatment_var) == 1)) == 0){
    stop("There are no (non)populist ads in the data.")
  }
  
  # Inverse probability weighting
  w.out.ipw <- weightit(
    formula = as.formula(str_c(treatment_var, " ~ ", paste(balancing_vars, collapse = " + "))),
    estimand = "ATE",
    data = data,
    method = "ebal")
  
  # Diagnostics
  balancing_tab <- bal.tab(w.out.ipw, stats = c("m", "v"), thresholds = c(m = .05))
  
  # Run regression model
  formula_adj <- as.formula(str_c(outcome_var, " ~ ", treatment_var, " * ", "(", paste(balancing_vars, collapse = " + "), ")"))
  lm_model_adj <- lm_weightit(formula_adj, data = data, weightit = w.out.ipw)
  
  # G-Computation for treatment effect
  ATE <- avg_comparisons(lm_model_adj, variables = treatment_var)
  
  # Return results
  output <- list(
    w.out.ipw = w.out.ipw,
    balancing_tab = balancing_tab,
    lm_model_adj = lm_model_adj,
    ATE = ATE
  )
  
  return(output)
}

```

# Compute difference measures

```{r}

# Enable parallel execution with optimal core usage
plan(multisession, workers = availableCores() - 1)

# Function to compute distance between actual and targeted distribution for a single ad
compute_single_ad_distance <- function(ad_row) {
    # We compute the following distance measures for age and gender:
    #   - Total Variation Distance (TVD)
    #   - Kulbach-Leibler Divergence (KL)
    #   - Wasserstein Distance (Wasserstein)
    #   - Chi-Square Distance (ChiSq)
  
  
  # Extract gender distributions
  target_gender <- c(ad_row$targeting_gender_distribution_female,
                     ad_row$targeting_gender_distribution_male)
  actual_gender <- c(ad_row$actual_gender_distribution_unique_views_female,
                     ad_row$actual_gender_distribution_unique_views_male)

  # Extract age distributions
  target_age <- c(ad_row$targeting_age_distribution_13_17,
                  ad_row$targeting_age_distribution_18_24,
                  ad_row$targeting_age_distribution_25_34, 
                  ad_row$targeting_age_distribution_35_44,
                  ad_row$targeting_age_distribution_45_54,
                  ad_row$targeting_age_distribution_55_64,
                  ad_row$targeting_age_distribution_65)

  actual_age <- c(ad_row$actual_age_distribution_unique_views_age_range_13_17_unique_views_share,
                  ad_row$actual_age_distribution_unique_views_age_range_18_24_unique_views_share,
                  ad_row$actual_age_distribution_unique_views_age_range_25_34_unique_views_share,
                  ad_row$actual_age_distribution_unique_views_age_range_35_44_unique_views_share,
                  ad_row$actual_age_distribution_unique_views_age_range_45_54_unique_views_share,
                  ad_row$actual_age_distribution_unique_views_age_range_55_64_unique_views_share,
                  ad_row$actual_age_distribution_unique_views_age_range_65_unique_views_share)

  # Safe normalization function
  normalize <- function(x) {
    total <- sum(x, na.rm = TRUE)
    if (is.na(total) || total == 0) {
      return(rep(NA, length(x)))  # return NA vector to signal undefined distribution
    } else {
      return(x / total)
    }
  }

  # Normalize distributions
  target_gender <- normalize(target_gender)
  actual_gender <- normalize(actual_gender)
  target_age <- normalize(target_age)
  actual_age <- normalize(actual_age)

  # If any normalized distribution is undefined, return NA for all metrics
  if (any(is.na(target_gender)) || any(is.na(actual_gender)) ||
      any(is.na(target_age))    || any(is.na(actual_age))) {
    return(tibble(
      id = ad_row$id,
      TVD_gender = NA_real_,
      KL_gender = NA_real_,
      Wasserstein_gender = NA_real_,
      ChiSq_gender = NA_real_,
      TVD_age = NA_real_,
      KL_age = NA_real_,
      Wasserstein_age = NA_real_,
      ChiSq_age = NA_real_
    ))
  }

  # Distance metrics for GENDER
  tvd_gender <- sum(abs(target_gender - actual_gender)) / 2
  kl_gender <- sum(ifelse(actual_gender > 0 & target_gender > 0,
                          actual_gender * log(actual_gender / target_gender), 0))
  wasserstein_gender <- wasserstein1d(target_gender, actual_gender)
  chi_gender <- sum(ifelse(target_gender > 0,
                           (target_gender - actual_gender)^2 / target_gender, 0))

  # Distance metrics for AGE
  tvd_age <- sum(abs(target_age - actual_age)) / 2
  kl_age <- sum(ifelse(actual_age > 0 & target_age > 0,
                       actual_age * log(actual_age / target_age), 0))
  wasserstein_age <- wasserstein1d(target_age, actual_age)
  chi_age <- sum(ifelse(target_age > 0,
                        (target_age - actual_age)^2 / target_age, 0))

  # Return results as a tidy tibble
  tibble(
    id = ad_row$id,
    TVD_gender = tvd_gender,
    KL_gender = kl_gender,
    Wasserstein_gender = wasserstein_gender,
    ChiSq_gender = chi_gender,
    TVD_age = tvd_age,
    KL_age = kl_age,
    Wasserstein_age = wasserstein_age,
    ChiSq_age = chi_age
  )
}

```

# Load data

```{r, include=FALSE, echo=FALSE}

# Load ad data
ad_data <- read_parquet(str_c(path_data, "ad_library/", "EU_2024_ad_library_preprocessed.parquet")) %>% as_tibble()

# Unnest targeting columns
ad_data <- ad_data %>%
  unnest_wider(targeting_gender_distribution, names_sep = "_") %>%
  unnest_wider(targeting_age_distribution, names_sep = "_") %>%
  unnest_wider(actual_gender_distribution_unique_views, names_sep = "_") %>%
  unnest_wider(actual_age_distribution_unique_views, names_sep = "_") 
  
ad_data <- ad_data %>%  
  rename_with(~str_replace_all(., "-", "_"), matches("targeting_age_distribution|actual_age_distribution_unique_views")) %>%
  rename_with(~ str_replace_all(., "\\+", ""), matches("targeting_age_distribution|actual_age_distribution_unique_views"))

# Vector of countries
countries <- ad_data %>% select(country) %>% distinct() %>% pull()

```

```{r}
# Load ad data
ad_data <- read_parquet("../../Code/analysis/ad_data") %>% as_tibble()
```

```{r}
```

```{r}

# Define covariates
ad_vars <- c("platform", "ad_duration_scaled", "n_active_ads_country_scaled", "party_ad", "sentiment", "weekday_start", "weekday_end")
targeting <- c(ad_data %>% select(contains("targeting_age_distribution") & !contains("13_17")) %>% colnames())

# Male user share for each country
male_share_country <- c("FB_male_total_country", "IG_male_total_country")

# "logit_positive_mean", "fear", "anger", "joy", "sadness", "surprise", "disgust"

# Define matching vars
covariates <- c(ad_vars, targeting)

```

# Prepare data for analysis

```{r}

model_df <- ad_data %>%
  filter(eu_parliament_2024 == 1) %>%
  filter(target_gender == "All") %>% # Filter ads that do not target a specific gender
  mutate(
    excess_male_audience = actual_gender_distribution_unique_views_male - actual_gender_distribution_unique_views_female,
    populist = as.integer(ifelse(is.na(populist), 0, populist)), # Create populist variable => all parties not classified in Populist are non-populist
    populist = factor(populist, levels = c(0, 1), labels = c("Non-populist", "Populist")),
    farright = as.integer(ifelse(is.na(farright), 0, farright)), # Create farright variable => all parties not classified in Populist are non-farright
    farleft = as.integer(ifelse(is.na(farleft), 0, farleft)), # Create farleft variable => all parties not classified in Populist are non-farleft
    extremist = ifelse(farright == 1, "Farright", ifelse(farleft == 1, "Farleft", "Center")), # Create extremist variable; 3-level factor Farleft, Center, Farright
    extremist = factor(extremist, levels = c("Center", "Farleft", "Farright"), labels = c("Center", "Farleft", "Farright")),
    platform = factor(platform, levels = c("FB_IG", "FB", "IG"), labels = c("Facebook and Instagram", "Facebook", "Instagram")),
    sentiment = factor(sentiment, levels = c("neutral", "positive", "negative"), labels = c("Neutral", "Positive", "Negative")),
    across(.cols = c(weekday_start, weekday_end), ~ as_factor(.x)),
    across(.cols = c(n_active_ads_country, ad_duration, spend), ~ scale(.x) %>% as.vector(), .names = "{.col}_scaled")
  )

```

```{r}
# Load model_df
model_df <- read_parquet("../../Code/analysis/model_df.parquet") %>% as_tibble()
```


```{r}
#write_parquet(model_df, sink = "model_df.parquet")
#write_parquet(ad_data, sink = "ad_data")
```


# Overlap between populist and extremist

```{r}

model_df %>% filter(populist == "Populist" & extremist %in% c("Farleft", "Farright")) %>% nrow()

# 
model_df %>% filter(populist == "Populist") %>% group_by(extremist) %>% summarize(n = n())

# Share of populist ads
model_df %>% group_by(populist) %>% summarize(n = n()/nrow(model_df))

```

# Descriptives of gender share by extremist

```{r}

## Extremist
# Plot gender share by extremist
plot_gender_extremist <- ggplot(model_df) +
  geom_density(aes(x = actual_gender_distribution_unique_views_male, fill = extremist), alpha = 0.5) +
  scale_fill_manual(values = extremist_colors, limits = c("Farleft", "Center", "Farright")) +
  xlab("Male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_extremist

# Plot gender share by extremist by country
plot_gender_extremist_country <- ggplot(model_df) +
  geom_density(aes(x = actual_gender_distribution_unique_views_male, fill = extremist), alpha = 0.5) +
  scale_fill_manual(values = extremist_colors, limits = c("Farleft", "Center", "Farright")) +
  facet_wrap(~country, scales = "free") +
  xlab("Male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_extremist_country

## Populist
# Plot gender share by populist
plot_gender_populist <- ggplot(model_df) +
  geom_density(aes(x = actual_gender_distribution_unique_views_male, fill = populist), alpha = 0.5) +
  scale_fill_manual(values = populist_colors) +
  xlab("Male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_populist

plot_gender_populist_country <- ggplot(model_df) +
  geom_density(aes(x = actual_gender_distribution_unique_views_male, fill = populist), alpha = 0.5) +
  scale_fill_manual(values = populist_colors) +
  facet_wrap(~country, scales = "free") +
  xlab("Male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_populist_country

```

# Plot excess male share

```{r}

## Extremist
# Plot gender share by extremist
plot_gender_extremist_excess <- ggplot(model_df) +
  geom_density(aes(x = excess_male_audience, fill = extremist), alpha = 0.5) +
  scale_fill_manual(values = extremist_colors, limits = c("Farleft", "Center", "Farright")) +
  xlab("Excess male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_extremist_excess

# Plot gender share by extremist by country
plot_gender_extremist_excess_country <- ggplot(model_df) +
  geom_density(aes(x = excess_male_audience, fill = extremist), alpha = 0.5) +
  scale_fill_manual(values = extremist_colors, limits = c("Farleft", "Center", "Farright")) +
  facet_wrap(~country, scales = "free") +
  xlab("Excess male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_extremist_excess_country

## Populist
# Plot gender share by populist
plot_gender_populist_excess <- ggplot(model_df) +
  geom_density(aes(x = excess_male_audience, fill = populist), alpha = 0.5) +
  scale_fill_manual(values = populist_colors) +
  xlab("Excess male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_populist_excess

plot_gender_populist_excess_country <- ggplot(model_df) +
  geom_density(aes(x = excess_male_audience, fill = populist), alpha = 0.5) +
  scale_fill_manual(values = populist_colors) +
  facet_wrap(~country, scales = "free") +
  xlab("Excess male audience (in %)") +
  ylab("") +
  theme(legend.position = "bottom",
        legned.direction = "horizontal")

plot_gender_populist_excess_country

```

# Set up map data

```{r}
# Map data
map_data <- read_sf(dsn = str_c(path_data, "misc/world_shape_files/ne_10m_admin_0_countries.shp")) %>% st_as_sf()

# Filter for EU countries and handle Cyprus
# Extract the geometry for Cyprus from map_data
cyprus_geometry <- map_data %>% 
  filter(str_detect(NAME, "Cyprus")) %>%
  mutate(ISO_A2_EH = "CY") %>% 
  group_by(ISO_A2_EH) %>%
  summarise() %>%
  st_geometry()

# Extract the geometry for EU countries
eu <- map_data %>% 
  filter(ISO_A2_EH %in% countries, TYPE %in% c("Country", "Sovereign country")) %>% 
  select(ISO_A2_EH, geometry) %>%
  mutate(
    geometry = case_when(
    ISO_A2_EH == "CY" ~ cyprus_geometry,
    TRUE ~ geometry),
    pattern = case_when(
      ISO_A2_EH %in% c("PT", "FR") ~ "crosshatch",
      TRUE ~ "stripe"
    )
  )

# Lambert Conformal Conic (EPSG:3035) - Europe-focused projection
lambert_crs <- 3035

# Define EU bounding box in Lambert CRS (roughly Europe)
xlim_europe <- c(2500000, 6500000)  # Adjusted for Europe (East-West)
ylim_europe <- c(1050000, 5300000)  # Adjusted for Europe (North-South)

# Countries to hatch
hatched_countries <- map_data %>%
  filter(ISO_A2_EH %in% c("FR", "PT"), TYPE %in% c("Country", "Sovereign country"))

# Set up base plot for map
map_base <- ggplot() +
  # Base map of world
  geom_sf(data = map_data, aes(geometry = geometry), fill = "lightgrey", color = "white", size = 0.1) +
  # Base map of Europe (with pattern for countries)
  geom_sf_pattern(data = eu %>% filter(!(ISO_A2_EH %in% c("FR", "PT"))), 
                  aes(geometry = geometry, pattern = pattern, pattern_fill = pattern, fill = pattern),
                  pattern_density = 0.2,
                  pattern_spacing = 0.03,
                  pattern_angle = 45,
                  pattern_color = "black",
                  fill = "lightgrey",
                  color = "white",
                  size = 0.1) +
  # Plot France and Portugal with different pattern
  geom_sf_pattern(data = eu %>% filter(ISO_A2_EH %in% c("FR", "PT")), 
                  aes(geometry = geometry, pattern = pattern, pattern_fill = pattern),
                  pattern_density = 0.5,
                  pattern_spacing = 0.03,
                  pattern_angle = 90,
                  pattern_color = "darkred",
                  fill = "lightgrey",
                  color = "white",
                  size = 0.1) +
  scale_pattern_manual(values = c("stripe" = "stripe", "crosshatch" = "stripe"), labels = c("Ads prohibited", "No data")) +
  scale_pattern_fill_manual(values = c("stripe" = "black", "crosshatch" = "darkred"), labels = c("Ads prohibited", "No data")) +
    theme(
    legend.position = "bottom",  # Position legends at the bottom
    legend.direction = "horizontal",  # Default horizontal arrangement
    axis.text.y = element_blank(),
    axis.text.x = element_blank(),
    legend.spacing.y = unit(0.1, "cm"),  # Add space between legends
    legend.box = "vertical",  # Stack the legends vertically
    legend.box.spacing = unit(0.5, "cm")  # Add space between the two legends
  )

```

# Extremist: Map of gender share across europe

```{r}

df_plot <- model_df %>% 
  group_by(country, extremist) %>% 
  summarize(excess_male_audience = mean(excess_male_audience, na.rm = TRUE),
            actual_gender_distribution_unique_views_male = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE)) %>%
  right_join(eu, by = c("country" = "ISO_A2_EH")) %>%
  mutate(extremist = fct_relevel(extremist, "Farleft", "Center", "Farright")) %>%
  drop_na() %>% # Drop Portugal and France
  st_as_sf()

# Plot map of share of male audience share by extremist
map_extremist_views_male <- map_base +
  geom_sf(data = df_plot, aes(geometry = geometry, fill = actual_gender_distribution_unique_views_male), color = "white", size = 0.1) +
  coord_sf(crs = lambert_crs, xlim = xlim_europe, ylim = ylim_europe) +
  scale_fill_viridis_c(
    direction = -1,
    option = "D",
    limits = c(0.4, 0.8),
    breaks = seq(0.4, 0.8, 0.1),
    labels = c("40%", "50%", "60%", "70%", "80%")
  ) +
  facet_wrap(~extremist, nrow = 1, ncol = 3) +
  guides(
    fill = guide_colorbar(barwidth = unit(10, "cm"), barheight = unit(0.5, "cm"), order = 1) 
  )

map_extremist_views_male
ggsave(str_c(path_figures, "map_views_male_extremist_new.pdf"), map_extremist_views_male, width = 20, height = 10, units = "cm")

# Plot map of excess male share by extremist
map_extremist_excess_male <- map_base +
  geom_sf(data = df_plot, aes(geometry = geometry, fill = excess_male_audience), color = "white", size = 0.1) +
  coord_sf(crs = lambert_crs, xlim = xlim_europe, ylim = ylim_europe) +
 # Divergent color scale
  scale_fill_gradient2(
    low = "darkred",       # Color for negative values (female-skewed)
    mid = "white",         # Color for exactly 0 (gender balanced)
    high = "darkblue",     # Color for positive values (male-skewed)
    midpoint = 0,          # Anchors the white color at 0
    limits = c(-0.2, 0.6),
    breaks = seq(-0.2, 0.6, 0.2),
    labels = c("-20%", "0%", "20%", "40%", "60%")
  ) +
  facet_wrap(~extremist, nrow = 1, ncol = 3) +
  guides(
    fill = guide_colorbar(barwidth = unit(10, "cm"), barheight = unit(0.5, "cm"), order = 1) 
  )

map_extremist_excess_male
ggsave(str_c(path_figures, "map_excess_views_male_extremist_new.pdf"), map_extremist_excess_male, width = 20, height = 10, units = "cm")

```

# Populist: Map of gender share across europe

```{r}

df_plot <- model_df %>% 
  group_by(country, populist) %>% 
  summarize(excess_male_audience = mean(excess_male_audience, na.rm = TRUE),
            actual_gender_distribution_unique_views_male = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE)) %>%
  right_join(eu, by = c("country" = "ISO_A2_EH")) %>%
  drop_na() %>% # Drop Portugal and France
  st_as_sf()

# Plot map of share of male audience share by populist
map_populist_views_male <- map_base +
  geom_sf(data = df_plot, aes(geometry = geometry, fill = actual_gender_distribution_unique_views_male), color = "white", size = 0.1) +
  coord_sf(crs = lambert_crs, xlim = xlim_europe, ylim = ylim_europe) +
  scale_fill_viridis_c(
    direction = -1,
    option = "D",
    limits = c(0.35, 0.75),
    breaks = seq(0.3, 0.8, 0.1),
    labels = c("", "40", "50%", "60%", "70%", "")
  ) +
  facet_wrap(~populist, nrow = 1, ncol = 3) +
  guides(
    fill = guide_colorbar(barwidth = unit(10, "cm"), barheight = unit(0.5, "cm"), order = 1) 
  )

map_populist_views_male
ggsave(str_c(path_figures, "map_views_male_populist.svg"), map_populist_views_male, width = 20, height = 10, units = "cm")

# Plot map of excess male share by populist
map_populist_excess_male <- map_base +
  geom_sf(data = df_plot, aes(geometry = geometry, fill = excess_male_audience), color = "white", size = 0.1) +
  coord_sf(crs = lambert_crs, xlim = xlim_europe, ylim = ylim_europe) +
  scale_fill_viridis_c(
    direction = -1,
    option = "D",
    limits = c(-0.25, 0.45),
    breaks = seq(-0.4, 0.6, 0.2),
    labels = c("", "-20%", "0%", "20%", "40%", "")
  ) +
  facet_wrap(~populist, nrow = 1, ncol = 3) +
  guides(
    fill = guide_colorbar(barwidth = unit(10, "cm"), barheight = unit(0.5, "cm"), order = 1) 
  )

map_populist_excess_male
ggsave(str_c(path_figures, "map_excess_views_male_populist.svg"), map_populist_excess_male, width = 20, height = 10, units = "cm")

```

# Estimate association between gender share and extremist/populist

```{r}

## Extremist
# Create formula
formula_extremist <- as.formula(str_c("actual_gender_distribution_unique_views_male" , " ~ ", "extremist", " + ", paste(covariates, collapse = " + "), " + country"))

# Estimate linear model
lm_extremist <- lm(formula = formula_extremist, data = model_df)

# Inference
inference_extremist <- coeftest(lm_extremist, .vcov = vcovCL(lm_extremist, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_extremist <- extract_coef_inference(inference_extremist)
coef_extremist

## Populist
# Create formula
formula_populist <- as.formula(str_c("actual_gender_distribution_unique_views_male" , " ~ ", "populist", " + ", paste(covariates, collapse = " + "), " + country"))

# Estimate linear model
lm_populist <- lm(formula = formula_populist, data = model_df)

# Inference
inference_populist <- coeftest(lm_populist, .vcov = vcovCL(lm_populist, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_populist <- extract_coef_inference(inference_populist)
coef_populist

```

# Visualize regression outcomes: Coefficient plots

```{r}

## Extremist
# Extract coefficients extremist
df_plot <- coef_extremist %>% filter(str_detect(term, "extremist")) %>% mutate(term = str_remove(term, "extremist"))

# Plot coefficients extremist
coeff_plot_extremist <- ggplot(data = df_plot, mapping = aes(x = term, y = estimate, fill = term, color = term, shape = term)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low.99, ymax = conf.high.99, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 0.6, size = 0.5) +
  geom_pointrange(aes(ymin = conf.low.95, ymax = conf.high.95, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 1.2, size = 0.5) +
  coord_flip() + labs(x = "", y = "") +
  scale_fill_manual(values = extremist_colors[c(1, 3)]) +
  scale_color_manual(values = extremist_colors[c(1, 3)]) +
  scale_shape_manual(values = c(21, 23)) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 18)) +
  ylab("Coefficient")

coeff_plot_extremist
ggsave(coeff_plot_extremist, filename = str_c(path_figures, "coeff_plot_extremist.pdf"), width = 10, height = 5, units = "cm")

## Populist
# Extract coefficients populist
df_plot <- coef_populist %>% filter(str_detect(term, "populist")) %>% mutate(term = "Populist")

# Plot coefficients populist
coeff_plot_populist <- ggplot(data = df_plot, mapping = aes(x = term, y = estimate, fill = term, color = term)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low.99, ymax = conf.high.99, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 0.6, size = 0.5, shape = 22) +
  geom_pointrange(aes(ymin = conf.low.95, ymax = conf.high.95, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 1.2, size = 0.5, shape = 22) +
  coord_flip() + labs(x = "", y = "") +
  scale_fill_manual(values = populist_colors[2]) +
  scale_color_manual(values = populist_colors[2]) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 18)) +
  ylab("Coefficient")

coeff_plot_populist
ggsave(coeff_plot_populist, filename = str_c(path_figures, "coeff_plot_populist.pdf"), width = 10, height = 5, units = "cm")


```

# Visualize regression outcomes: Effect plots

```{r}

## Extremist
# Predict marginal effects
gge_extremist <- predict_response(model = lm_extremist_media, terms = "extremist", vcov_fun = vcovCL(lm_extremist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE))

# Plot extremist effect
plot_effect_extremist <- ggplot(gge_extremist, aes(x = fct_relevel(x, "Farleft", "Center", "Farright"), y = predicted)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = x), width = 0.1) +
  geom_point(aes(color = x), size = 1.5) +
  scale_color_manual(values = extremist_colors) +
  xlab("") +
  #ylab("Share of unique views by men") +
  ylab("Predicted excess male share") +
  theme(legend.position = "none")

plot_effect_extremist
ggsave(plot_effect_extremist, filename = str_c(path_figures, "plot_effect_extremist.pdf"), width = 10, height = 10, units = "cm")

## Populist
# Predict marginal effects
gge_populist <- predict_response(lm_populist_media, terms = "populist", vcov_fun = vcovCL(lm_populist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE))

# Plot populist effect
plot_effect_populist <- ggplot(gge_populist, aes(x = x, y = predicted)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = x), width = 0.2,linewidth = 1) +
  geom_point(aes(color = x), size = 3) +
  scale_color_manual(values = populist_colors) +
  xlab("") +
  #ylab("Share of unique views by men") +
  ylab("Predicted excess male share") +
  theme(legend.position = "none")

plot_effect_populist
ggsave(plot_effect_populist, filename = str_c(path_figures, "plot_effect_populist.pdf"), width = 10, height = 10, units = "cm")

```

# Per country analysis

```{r}

## Extremist
# Estimate linear model for each country
lm_extremist_country <- map(countries, ~estimate_country(data = model_df, country_code = .x, dep_var = "actual_gender_distribution_unique_views_male", indep_vars = c("extremist", covariates), vcov_type = "HC1"))

# Extract coefficients
coef_extremist_country <- map_dfr(lm_extremist_country, ~ if(!is.null(.x)){.x$coef_df %>% filter(str_detect(term, "extremistFarright|extremistFarleft"))})

## Populist
# Estimate linear model for each country
lm_populist_country <- map(countries, ~estimate_country(data = model_df, country_code = .x, dep_var = "actual_gender_distribution_unique_views_male", indep_vars = c("populist", covariates), vcov_type = "HC1"))

# Extract coefficients
coef_populist_country <- map_dfr(lm_populist_country, ~ if(!is.null(.x)){.x$coef_df %>% filter(str_detect(term, "populist"))})

# Results: Coefficients are consistent with main analysis for most countries
# => Farright positive in most cases and > farleft
# => Populist positive in most cases

```

# Visualize regression outcomes (per country): Coefficient plots

```{r}

## Extremist
# Plot coefficients
df_plot <- coef_extremist_country %>% mutate(term = str_replace(term, "extremist", ""))

coeff_plot_extremist_country <- ggplot(data = df_plot, mapping = aes(x = country, y = estimate, fill = term, color = term, shape = term)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low.99, ymax = conf.high.99, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 0.6, size = 0.5) +
  geom_pointrange(aes(ymin = conf.low.95, ymax = conf.high.95, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 1.2, size = 0.5) +
  coord_flip() +
  scale_fill_manual(values = extremist_colors[c(1, 3)]) +
  scale_color_manual(values = extremist_colors[c(1, 3)]) +
  scale_shape_manual(values = c(21, 23)) +
  labs(x = "", y = "Coefficient") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        panel.grid.minor = element_blank(),
        text = element_text(size = 18))

coeff_plot_extremist_country
ggsave(coeff_plot_extremist_country, filename = str_c(path_figures, "coeff_plot_extremist_country.pdf"))

## Populist
# Plot coefficients
df_plot <- coef_populist_country %>% mutate(term = str_replace(term, "populist", ""))

coeff_plot_populist_country <- ggplot(data = df_plot, mapping = aes(x = country, y = estimate, fill = term, color = term, shape = term)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low.99, ymax = conf.high.99, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 0.6, size = 0.5) +
  geom_pointrange(aes(ymin = conf.low.95, ymax = conf.high.95, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 1.2, size = 0.5) +
  coord_flip() +
  scale_fill_manual(values = populist_colors[2]) +
  scale_color_manual(values = populist_colors[2]) +
  scale_shape_manual(values = c(22)) +
  labs(x = "", y = "Coefficient") +
  theme(legend.position = "right",
        legend.direction = "vertical",
        panel.grid.minor = element_blank(),
        text = element_text(size = 18))

coeff_plot_populist_country
ggsave(coeff_plot_populist_country, filename = str_c(path_figures, "coeff_plot_populist_country.pdf"))

```

# Robustness check: Include share of male users per country

```{r}

#Note: We need to exclude country fixed effects for this analysis to avoid multicollinearity

dep_var <- "excess_male_audience"
 #dep_var <- "actual_gender_distribution_unique_views_male"   # current main-code version


## Extremist
# Create formula
formula_extremist_male <- as.formula(str_c(dep_var , " ~ ", "extremist", " + ", paste(c(covariates_media, male_share_country), collapse = " + ")))

# Estimate linear model
lm_extremist_male <- lm(formula = formula_extremist_male, data = model_df_media)

# Inference
inference_extremist_male <- coeftest(lm_extremist_male, .vcov = vcovCL(lm_extremist_male, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_extremist_male <- extract_coef_inference(inference_extremist_male)
coef_extremist_male

## Populist
# Create formula
formula_populist_male <- as.formula(str_c(dep_var , " ~ ", "populist", " + ", paste(c(covariates_media, male_share_country), collapse = " + ")))

# Estimate linear model
lm_populist_male <- lm(formula = formula_populist_male, data = model_df_media)

# Inference
inference_populist_male <- coeftest(lm_populist_male, .vcov = vcovCL(lm_populist_male, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_populist_male <- extract_coef_inference(inference_populist_male)
coef_populist_male

# Results: Coefficients are consistent with main analysis
# => positive and significant coefficient for farright; negative and significant coefficient for farleft
# => positive and significant coefficient for populist

```

# Robustness check: Beta regression

```{r}

# Note: Very few instances of our dependent variable are 0 or 1 (485/115814); To use a beta regression we need to transform the dependent variable
# The transformation leaves most values unchanged; rank/order and variation are preserved

# Transform dependent variable
n = length(model_df)
df_model_beta <- model_df %>% mutate(actual_gender_distribution_unique_views_male = (actual_gender_distribution_unique_views_male * (n - 1) + 0.5) / n)

## Extremist
# Estimate beta regression
beta_extremist <- betareg(formula_extremist, data = df_model_beta, link = "logit")

# Inference
inference_beta_extremist <- coeftest(beta_extremist, .vcov = vcovCL(beta_extremist, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_beta_extremist <- extract_coef_inference(inference_beta_extremist)
coef_beta_extremist

## Populist
# Estimate beta regression
beta_populist <- betareg(formula_populist, data = df_model_beta, link = "logit")

# Inference
inference_beta_populist <- coeftest(beta_populist, .vcov = vcovCL(beta_populist, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_beta_populist <- extract_coef_inference(inference_beta_populist)
coef_beta_populist

# Results: Coefficients are consistent with main analysis
# => positive and significant coefficient for farright; negative and significant coefficient for farleft
# => positive and significant coefficient for populist

```

# Robustness check: Fractional logit regression

```{r}

## Extremist
# Estimate fractional logit regression
fl_extremist <- glm(formula_extremist, data = model_df, family = quasibinomial(link = "logit"))

# Inference
inference_fl_extremist <- coeftest(fl_extremist, .vcov = vcovCL(fl_extremist, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_fl_extremist <- extract_coef_inference(inference_fl_extremist)
coef_fl_extremist

## Populist
# Estimate fractional logit regression
fl_populist <- glm(formula_populist, data = model_df, family = quasibinomial(link = "logit"))
coeff_plot_populist <- coeftest(fl_populist, .vcov = vcovHC(fl_populist, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_fl_populist <- extract_coef_inference(coeff_plot_populist)
coef_fl_populist

# Results: Coefficients are consistent with main analysis
# => positive and significant coefficient for farright; negative and significant coefficient for farleft
# => positive and significant coefficient for populist

```

# Robustness check: Propensity score matching

```{r}

# Propensity score matching for extremist
psm_populist <- perform_psm(data = model_df_media, 
                       balancing_vars = c(covariates_media, "country"), 
                       treatment_var = "populist", 
                       outcome_var = "actual_gender_distribution_unique_views_male")


print(psm_populist$balancing_tab)
plot(summary(psm_populist$match_out))
plot(psm_populist$match_out, type = "hist")
summary(psm_populist$lm_model_adj)
print(psm_populist$ATE)

# Results: ATE is consistent with results from main analysis
# => positive and significant ATE for populist; Also, the adjusted model shows a positive and significant coefficient for populist

```

```{r}
print(psm_populist$balancing_tab)
summary(psm_populist$lm_model_adj)
```


# Robustness check: Different dependent variabel (Excess male audience = Share male views - share female views)

```{r}

## Extremist
# Create formula
formula_extremist_dep <- as.formula(str_c("excess_male_audience" , " ~ ", "extremist", " + ", paste(c(covariates), collapse = " + "), " + country"))

# Estimate linear model
lm_extremist_dep <- lm(formula = formula_extremist_dep, data = model_df)

# Inference
inferece_extremist_dep <- coeftest(lm_extremist_dep, .vcov = vcovCL(lm_extremist_dep, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_extremist_dep <- extract_coef_inference(inferece_extremist_dep)
coef_extremist_dep

## Populist
# Create formula
formula_populist_dep <- as.formula(str_c("excess_male_audience" , " ~ ", "populist", " + ", paste(c(covariates), collapse = " + "), " + country"))

# Estimate linear model
lm_populist_dep <- lm(formula = formula_populist_dep, data = model_df)

# Inference
inferece_populist_dep <- coeftest(lm_populist_dep, vcov = vcovCL(lm_populist_dep, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_populist_dep <- extract_coef_inference(inferece_populist_dep)
coef_populist_dep

```

# Compute targeting vs. actual discrepencies

```{r}

# Compute distances in parallel
#distance_data <- compute_distribution_distances(ad_data)
#write_parquet(distance_data, sink = "targeting_actual_distance.parquet")
#distance_data <- read_parquet("targeting_actual_distance.parquet")


# Join with original dataset
ad_data <- ad_data %>%
  left_join(distance_data, by = "id")

```

# Check female advantage

```{r}

model_df <- ad_data %>%
  filter(eu_parliament_2024 == 1) %>%
  filter(target_gender == "All") %>% # Filter ads that do not target a specific gender
  mutate(
    populist = as.integer(ifelse(is.na(populist), 0, populist)), # Create populist variable => all parties not classified in Populist are non-populist
    farright = as.integer(ifelse(is.na(farright), 0, farright)), # Create farright variable => all parties not classified in Populist are non-farright
    farleft = as.integer(ifelse(is.na(farleft), 0, farleft)), # Create farleft variable => all parties not classified in Populist are non-farleft
    extremist = ifelse(farright == 1, "Farright", ifelse(farleft == 1, "Farleft", "Center")), # Create extremist variable; 3-level factor Farleft, Center, Farright
    across(.cols = c(weekday_start, weekday_end), ~ as_factor(.x)),
    across(.cols = c(unique_views_spend, impressions_spend), ~ log(.x), .names = "{.col}_log"),
    across(.cols = c(n_active_ads_country, ad_duration, negative, positive, starts_with("targeting_gender"), starts_with("targeting_age")), ~ scale(.x) %>% as.vector())
  )

```

# Create modeling dataframe

```{r}

model_df <- ad_data %>%
  filter(eu_parliament_2024 == 1) %>% # Only use parties that made it into parliament
  mutate(
    populist = as.integer(ifelse(is.na(populist), 0, populist)), # Create populist variable => all parties not classified in Populist are non-populist
    farright = as.integer(ifelse(is.na(farright), 0, farright)), # Create farright variable => all parties not classified in Populist are non-farright
    farleft = as.integer(ifelse(is.na(farleft), 0, farleft)), # Create farleft variable => all parties not classified in Populist are non-farleft
    extremist = ifelse(farright == 1, "Farright", ifelse(farleft == 1, "Farleft", "Center")), # Create extremist variable; 3-level factor Farleft, Center, Farright
    female_advantage = 
    across(.cols = c(weekday_start, weekday_end), ~ as_factor(.x)),
    across(.cols = c(unique_views_spend, impressions_spend), ~ log(.x), .names = "{.col}_log"),
    across(.cols = c(n_active_ads_country, ad_duration, negative, positive, starts_with("targeting_gender"), starts_with("targeting_age")), ~ scale(.x) %>% as.vector())
  )

```

# Analyze discrepencies

```{r}

# Density of gender discrepency by populist
ggplot(model_df) +
  geom_density(aes(x = TVD_gender, fill = factor(populist)), alpha = 0.5) +
  facet_wrap(~country, scales = "free") +
  theme(legend.position = "right",
        legend.direction = "vertical")


# Density of age discrepency by populist
ggplot(model_df) +
  geom_density(aes(x = Wasserstein_age, fill = factor(populist)), alpha = 0.5) +
  facet_wrap(~country, scales = "free") +
  theme(legend.position = "right",
        legend.direction = "vertical")

# Density of gender discrepency by extremist
ggplot(model_df) +
  geom_density(aes(x = TVD_gender, fill = factor(extremist)), alpha = 0.5) +
  facet_wrap(~country, scales = "free") +
  theme(legend.position = "right",
        legend.direction = "vertical")


# Density of age discrepency by extremist
ggplot(model_df) +
  geom_density(aes(x = log(unique_views_spend), fill = factor(extremist)), alpha = 0.5) +
  facet_wrap(~country, scales = "free") +
  theme(legend.position = "right",
        legend.direction = "vertical")

```
# Analyse negativity
# Descriptives

```{r}

# Summary statistics for negative sentiment
ad_data %>% summarize(
  mean_negative = mean(negative, na.rm = TRUE),
  sd_negative = sd(negative, na.rm = TRUE),
  median_negative = median(negative, na.rm = TRUE),
  min_negative = min(negative, na.rm = TRUE),
  max_negative = max(negative, na.rm = TRUE),
)

# Categorical sentiment
ad_data %>%
  group_by(sentiment) %>%
  summarize(n_ads = n())

# by country
ad_data %>%
  group_by(country, sentiment) %>%
  summarize(n_ads = n())

# Sentiment data
sentiment_df <- ad_data %>% filter(!is.na(sentiment)) %>% mutate(sentiment = factor(sentiment, levels = c("neutral", "negative", "positive")))

```

# Some plots

```{r}

# Distribution of sentiment
plot_dist_negative <- ggplot(data = sentiment_df) +
  geom_density(aes(x = log(unique_views_spend), fill = sentiment), alpha = 0.5) +
  labs(title = "Distribution of unique views spend by sentiment",
       x = "ln(Unique views spend)",
       y = "Density",
       fill = "Sentiment") +
  theme(legend.position = "right",
        legend.direction = "vertical")

plot_dist_negative

# Distribution of sentiment by country
plot_dist_country_negative <- ggplot(data = sentiment_df) +
  geom_density(aes(x = log(unique_views_spend), fill = sentiment), alpha = 0.5) +
  facet_wrap(~country, scales = "free") +
  labs(title = "Distribution of unique views spend by sentiment",
       x = "ln(Unique views spend)",
       y = "Density",
       fill = "Sentiment") +
  theme(legend.position = "right",
        legend.direction = "vertical")

plot_dist_country_negative

```

# Unique views per EUR by sentiment

```{r}

lm_sentiment <- map(countries, ~estimate_country(data = sentiment_df, country_code = .x, dep_var = "unique_views_spend", indep_vars = c("sentiment", covariates)))
names(lm_sentiment) <- countries

# Extract coefficients for sentiment
sentiment <- map_dfr(lm_sentiment, ~ .x$coef_df %>% filter(str_detect(term, "sentiment")))

# Plot coefficients
df_plot <- sentiment %>%
  mutate(
    negative_coef = ifelse(estimate < 0, "Negative", "Positive"),  # Identify negative estimates
    sig_stars = case_when(  # Assign significance stars
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      TRUE ~ ""  # No stars for non-significant estimates
    )
  ) %>%
  filter(term == "sentimentpositive")

# Create the bar plot with significance stars
plot_sentiment <- ggplot(data = df_plot, aes(x = country, y = estimate, fill = negative_coef)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +  # Bars with black borders
  
  # Add significance stars as text labels above bars
  geom_text(aes(label = sig_stars, y = estimate + 0.05 * max(abs(estimate))),  # Offset text slightly above bars
            size = 3) +
  
  scale_fill_manual(values = c("red", "blue")) +
  labs(title = "Negative Sentiment Effects by Country",
       x = "Country",
       y = "Estimate",
       fill = "Negative Coefficient") +
  theme_minimal() +
  theme(legend.position = "none",
        legend.direction = "vertical")

plot_sentiment

```

# Unique views for negative

```{r}

lm_negative <- map(countries, ~estimate_country(data = sentiment_df, country_code = .x, dep_var = "unique_views_spend", indep_vars = c("negative", "positive", covariates, "national_party")))
names(lm_negative) <- countries

# Extract coefficients for sentiment
negative <- map_dfr(lm_negative, ~ .x$coef_df %>% filter(str_detect(term, "negative|positive")))

# Plot coefficients
df_plot <- negative %>%
  mutate(
    negative = ifelse(estimate < 0, "Negative", "Positive"),  # Identify negative estimates
    sig_stars = case_when(  # Assign significance stars
      p.value < 0.001 ~ "***",
      p.value < 0.01 ~ "**",
      p.value < 0.05 ~ "*",
      TRUE ~ ""  # No stars for non-significant estimates
    )
  ) %>%
  filter(term == "negative")

# Create the bar plot with significance stars
plot_negative <- ggplot(data = df_plot, aes(x = country, y = estimate, fill = negative)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +  # Bars with black borders
  
  # Add significance stars as text labels above bars
  geom_text(aes(label = sig_stars, y = estimate + 0.05 * max(abs(estimate))),  # Offset text slightly above bars
            size = 3) +
  
  scale_fill_manual(values = c("red", "blue")) +
  labs(title = "Negative Sentiment Effects by Country",
       x = "Country",
       y = "Estimate",
       fill = "Sign of Coefficient") +
  theme_minimal() +
  theme(legend.position = "right",
        legend.direction = "vertical")

plot_negative

```


# Populist analysis
## Set up dataframe

```{r}

# Create dataframe of populist ads
populist_df <- ad_data %>%
  filter(eu_parliament_2024 == 1) %>%
  mutate(
    populist = as.integer(ifelse(is.na(populist), 0, populist)),
    across(.cols = c(weekday_start, weekday_end), ~ as_factor(.x)),
    across(.cols = c(unique_views_spend, impressions_spend), ~ log(.x), .names = "{.col}_log"),
    across(.cols = c(n_active_ads_country, ad_duration, negative, positive, starts_with("targeting_gender"), starts_with("targeting_age")), ~ scale(.x) %>% as.vector())
  ) %>%
  rename_with(~str_replace(., "-", "_"), contains("targeting_age_distribution")) %>%
  rename_with(~str_replace(., "\\+", ""), contains("targeting_age_distribution"))

```

```{r}

# Number of populist ads
populist_df %>%
  group_by(populist) %>%
  summarize(n_ads = n())

# Number of populist ads per country
populist_df %>%
  group_by(country, populist) %>%
  summarize(n_ads = n())

# Populist parties
populist_df %>%
  filter(populist == 1) %>%
  select(national_party) %>%
  distinct()


```

# Some plots

```{r}

# Distribution of unique_views_spend by populist
plot_dist <- ggplot(data = populist_df, aes(x = log(unique_views_spend), fill = factor(populist))) +
  geom_density(alpha = 0.5) +
  labs(title = "Distribution of unique views spend by populist",
       x = "Unique views spend",
       y = "Density",
       fill = "Populist") +
  theme(legend.position = "top")

plot_dist

# Distribution by country
plot_dist_country <- ggplot(data = populist_df, aes(x = log(unique_views_spend), fill = factor(populist))) +
  geom_density(alpha = 0.5) +
  facet_wrap(~country) +
  labs(title = "Distribution of unique views spend by populist",
       x = "ln(Unique views spend)",
       y = "Density",
       fill = "Populist") +
  theme(legend.position = "right",
        legend.direction = "vertical")

ggsave(plot_dist_country, file = str_c(path_figures, "unique_views_spend_density_populist_country.pdf"), width = 25, height = 20, units = "cm")

```

# Fit linear model (Populist vs. non-populist)

```{r}

formula <- as.formula(str_c("unique_views_spend ~ populist + ", paste(matching_vars, collapse = " + "), "+ positive * populist + negative * populist"))
formula_country <- as.formula(str_c("unique_views_spend ~ populist + ", paste(matching_vars, collapse = " + "), "+ country + positive * populist + negative * populist"))

# Fit linear model
lm_model <- lm(formula, data = populist_df)
summary(lm_model, robust = TRUE)

# Country fixed effects
lm_country <- lm(formula_country, data = populist_df)
summary(lm_country, robust = TRUE)

```

# Random effects model (Populist vs. non-populist)

```{r}

formula_country_re <- as.formula(str_c("unique_views_spend ~ populist + ", paste(matching_vars, collapse = " + "), "+ (1 | country)"))
formula_country_pop <- as.formula(str_c("unique_views_spend ~ populist + ", paste(matching_vars, collapse = " + "), "+ (populist | country)"))

# Random effects model
# Random intercepts for country
lm_re <- lmer(formula_country_re, data = populist_df, REML = FALSE)
summary(lm_re)

# Random intercepts and random slopes for populist
lm_re_pop <- lmer(formula_country_pop, data = populist_df, REML = FALSE)
summary(lm_re_pop)

```

# Perform propensity score matching (Populist vs. non-populist)

```{r}
matching_vars = covariates_media

ipw <- perform_ipw(data = populist_df, 
                       balancing_vars = matching_vars, 
                       treatment_var = "populist", 
                       outcome_var = "unique_views_spend")

print(ipw$balancing_tab)
love.plot(ipw$w.out.ipw, thresholds = c(m = 0.1))
plot(summary(ipw$w.out.ipw))
print(ipw$ATE)


psm <- perform_psm(data = populist_df, 
                       balancing_vars = matching_vars, 
                       treatment_var = "populist", 
                       outcome_var = "unique_views_spend")


print(psm$balancing_tab)
plot(summary(psm$match_out))
plot(psm$match_out, type = "hist")
summary(psm$lm_model_adj)
print(psm$ATE)


```

# Logged dependent variable

```{r}

formula_log <- as.formula(str_c("unique_views_spend_log ~ populist + ", paste(matching_vars, collapse = " + ")))
formula_country_log <- as.formula(str_c("unique_views_spend_log ~ populist + ", paste(matching_vars, collapse = " + "), "+ country + positive * populist + negative * populist"))
formula_country_re_log <- as.formula(str_c("unique_views_spend_log ~ populist + ", paste(matching_vars, collapse = " + "), "+ (1 | country)"))
formula_country_pop_log <- as.formula(str_c("unique_views_spend_log ~ populist + ", paste(matching_vars, collapse = " + "), "+ (populist | country)"))

# Fit linear model
lm_model_log <- lm(formula_log, data = populist_df)
summary(lm_model_log, robust = TRUE)

# Country fixed effects
lm_country_log <- lm(formula_country_log, data = populist_df)
summary(lm_country_log, robust = TRUE)

# Random effects model
# Random intercepts for country
lm_re_log <- lmer(formula_country_re_log, data = populist_df, REML = FALSE)
summary(lm_re_log)

# Random intercepts and random slopes for populist
lm_re_pop_log <- lmer(formula_country_pop_log, data = populist_df, REML = FALSE)
summary(lm_re_pop_log)

```


```{r}

ggplot(populist_df, aes(x = logit_positive_mean), fill = populist) +
  geom_density(alpha = 0.5) #+
  #
  labs(title = "Distribution of positive sentiment by populist",
       x = "Positive sentiment",
       y = "Density",
       fill = "populist")

formula_persuasiveness <- as.formula(str_c("unique_views_spend ~ populist + ", paste(matching_vars, collapse = " + "), "+ logit_positive_mean + country"))

# Persuasiveness variable
lm_model_persuasiveness <- lm(formula_persuasiveness, data = populist_df)
summary(lm_model_persuasiveness, robust = TRUE)

```

## Data with farright variable

```{r}

# Create dataframe of fahrright ads
extremist_df <- ad_data %>%
  filter(eu_parliament_2024 == 1) %>%
  mutate(
    farright = as.integer(ifelse(is.na(farright), 0, farright)),
    farleft = as.integer(ifelse(is.na(farleft), 0, farleft)),
    extremist = ifelse(farright == 1, "Farright", ifelse(farleft == 1, "Farleft", "Center")),
    #extremist = factor(
    #ifelse(farright == 1, "Farright", ifelse(farleft == 1, "Farleft", "Center")),
    #levels = c("Center", "Farleft", "Farright") # Ensures "Center" is the base
  #),
    across(.cols = c(weekday_start, weekday_end), ~ as_factor(.x)),
    across(.cols = c(unique_views_spend, impressions_spend), ~ log(.x), .names = "{.col}_log"),
    across(.cols = c(n_active_ads_country, ad_duration, negative, positive, starts_with("targeting")), ~ scale(.x) %>% as.vector())) %>%
  rename_with(~str_replace(., "-", "_"), contains("targeting_age_distribution")) %>%
  rename_with(~str_replace(., "\\+", ""), contains("targeting_age_distribution"))

```

# Farleft vs. farright parties

```{r}

# Number of farright and farleft ads
extremist_df %>%
  group_by(extremist) %>%
  summarize(n_ads = n())

# Parties in each category
extremist_df %>%
  filter(extremist != "Center") %>%
  group_by(extremist) %>%
  select(national_party) %>%
  distinct()

```

# Some plots

```{r}

# Distribution of unique_views_spend by farright vs farleft
plot_dist_extreme <- ggplot(data = extremist_df, aes(x = log(unique_views_spend), fill = extremist)) +
  geom_density(alpha = 0.5) +
  labs(title = "Distribution of unique views spend by farright",
       x = "Unique views spend",
       y = "Density",
       fill = "Farright") +
  theme(legend.position = "top")

plot_dist_extreme

# Left-right score
df_plot <- extremist_df %>%
  filter(!is.na(left_right)) %>%
  group_by(country) %>%
  summarize(mean_left_right = mean(left_right, na.rm = TRUE),
            mean_unique_views_spend = mean(log(unique_views_spend), na.rm = TRUE))

plot_scatter_lr <- ggplot(data = df_plot, aes(x = mean_left_right, y = mean_unique_views_spend, color = country)) +
  geom_point(alpha = 0.5, size = 3) +  # Points
  geom_text_repel(aes(label = country), size = 4, max.overlaps = 15) +  # Labels
  labs(title = "Unique views spend by left-right score",
       x = "Left-right score",
       y = "Unique views spend",
       color = "Country") +
  theme(legend.position = "none")

plot_scatter_lr

# Left-right score by party
df_plot <- extremist_df %>%
  filter(!is.na(left_right)) %>%
  group_by(national_party) %>%
  summarize(mean_left_right = mean(left_right, na.rm = TRUE),
            mean_unique_views_spend = mean(log(unique_views_spend), na.rm = TRUE),
            extremist = first(extremist))

plot_scatter_lr_party <- ggplot(data = df_plot, aes(x = mean_left_right, y = mean_unique_views_spend, shape = extremist, color = extremist)) +
  geom_point(alpha = 0.5, size = 3) +  # Points
  labs(title = "Unique views spend by left-right score",
       x = "Left-right score",
       y = "Unique views spend")

plot_scatter_lr_party

plot_dist_country_extremist <- ggplot(data = extremist_df, aes(x = log(unique_views_spend), fill = factor(extremist))) +
  geom_density(alpha = 0.5) +
  facet_wrap(~country) +
  labs(title = "Distribution of unique views spend by Farleft vs. Farright",
       x = "ln(Unique views spend)",
       y = "Density",
       fill = "Extremist") +
  theme(legend.position = "right",
        legend.direction = "vertical")

ggsave(str_c(path_figures, "unique_views_spend_density_extremist_country.pdf"), plot_dist_country_extremist, width = 25, height = 20, units = "cm")

```

# Fit linear model (Farright vs. farleft)

```{r}

formula_extreme <- as.formula(str_c("unique_views_spend ~ extremist + ", paste(matching_vars, collapse = " + ")))
formula_country_extreme <- as.formula(str_c("unique_views_spend ~ extremist + ", paste(matching_vars, collapse = " + "), "+ country"))

# Fit linear model
lm_model_extreme <- lm(formula_extreme, data = extremist_df)
summary(lm_model_extreme, robust = TRUE)

# Country fixed effects
lm_country_extreme <- lm(formula_country_extreme, data = extremist_df)
summary(lm_country_extreme, robust = TRUE)

```

# Random effects model (Farright vs. farleft)

```{r}

formula_country_re_extreme <- as.formula(str_c("unique_views_spend ~ extremist + ", paste(matching_vars, collapse = " + "), "+ (1 | country)"))
formula_country_pop_extreme <- as.formula(str_c("unique_views_spend ~ extremist + ", paste(matching_vars, collapse = " + "), "+ (extremist | country)"))

# Random effects model
# Random intercepts for country
lm_re_extreme <- lmer(formula_country_re_extreme, data = extremist_df, REML = FALSE)
summary(lm_re_extreme)

# Random intercepts and random slopes for populist
lm_re_pop_extreme <- lmer(formula_country_re_extreme, data = extremist_df, REML = FALSE)
summary(lm_re_extreme)

```

# Farright vs. Farleft parties

```{r}

formula_by_country <- as.formula(str_c("unique_views_spend_log ~ extremist + ", paste(matching_vars, collapse = " + ")))

# Run linear model for each country
lm_countries <- map(set_names(countries), ~estimate_country(.x, extremist_df))

# Extract farleft and farright coefficients
farleft <- map2_dfr(names(lm_countries), lm_countries, ~{
  if (!is.null(.y)){  # .y represents the lm object
    coef_df <- broom::tidy(coeftest(.y, vcov = vcovHC(.y, type = "HC0")), conf.level = 0.95, conf.int = TRUE)
    
    if (coef_df %>% filter(term == "extremistFarleft") %>% nrow() > 0){
      coef_df <- coef_df %>% filter(term == "extremistFarleft") %>%
        mutate(country = .x)  # Assign country name correctly
      return(coef_df)
    } else {
      return(NULL)
    }
  } else {
    NULL
  }
})

farright <- map2_dfr(names(lm_countries), lm_countries, ~{
  if (!is.null(.y)){  # .y represents the lm object
    coef_df <- broom::tidy(coeftest(.y, vcov = vcovHC(.y, type = "HC0")), conf.level = 0.95, conf.int = TRUE)
    
    if (coef_df %>% filter(term == "extremistFarright") %>% nrow() > 0){
      coef_df <- coef_df %>% filter(term == "extremistFarright") %>%
        mutate(country = .x)  # Assign country name correctly
      return(coef_df)
    } else {
      return(NULL)
    }
  } else {
    NULL
  }
})

negative <- map2_dfr(names(lm_countries), lm_countries, ~{
  if (!is.null(.y)){  # .y represents the lm object
    coef_df <- broom::tidy(coeftest(.y, vcov = vcovHC(.y, type = "HC0")), conf.level = 0.95, conf.int = TRUE)
    
    if (coef_df %>% filter(term == "negative") %>% nrow() > 0){
      coef_df <- coef_df %>% filter(term == "negative") %>%
        mutate(country = .x)  # Assign country name correctly
      return(coef_df)
    } else {
      return(NULL)
    }
  } else {
    NULL
  }
})

```

Left-right score

```{r}

formula_by_country <- as.formula(str_c("unique_views_spend ~ left_right + ", paste(matching_vars, collapse = " + ")))

# Run linear model for each country
lm_countries_lr <- map(set_names(countries), ~estimate_country(.x, extremist_df))

left_right <- map2_dfr(names(lm_countries_lr), lm_countries_lr, ~{
  if (!is.null(.y)){  # .y represents the lm object
    coef_df <- broom::tidy(coeftest(.y, vcov = vcovHC(.y, type = "HC0")), conf.level = 0.95, conf.int = TRUE)
    
    if (coef_df %>% filter(term == "left_right") %>% nrow() > 0){
      coef_df <- coef_df %>% filter(term == "left_right") %>%
        mutate(country = .x)  # Assign country name correctly
      return(coef_df)
    } else {
      return(NULL)
    }
  } else {
    NULL
  }
})

ggplot(left_right) + geom_boxplot(aes(estimate))

negative <- map2_dfr(names(lm_countries_lr), lm_countries_lr, ~{
  if (!is.null(.y)){  # .y represents the lm object
    coef_df <- broom::tidy(coeftest(.y, vcov = vcovHC(.y, type = "HC0")), conf.level = 0.95, conf.int = TRUE)
    
    if (coef_df %>% filter(term == "negative") %>% nrow() > 0){
      coef_df <- coef_df %>% filter(term == "negative") %>%
        mutate(country = .x)  # Assign country name correctly
      return(coef_df)
    } else {
      return(NULL)
    }
  } else {
    NULL
  }
})

```


# Perform propensity score matching (Farleft vs. farright)

```{r}

ipw_farright <- perform_ipw(data = extremist_df, 
                       balancing_vars = matching_vars, 
                       treatment_var = "farright", 
                       outcome_var = "unique_views_spend")

print(ipw$balancing_tab)
love.plot(ipw$w.out.ipw, thresholds = c(m = 0.1))
plot(summary(ipw$w.out.ipw))
print(ipw$ATE)


psm_farright <- perform_psm(data = extremist_df, 
                       balancing_vars = matching_vars, 
                       treatment_var = "farright",
                       outcome_var = "unique_views_spend")


print(psm_farright$balancing_tab)
plot(summary(psm_farright$match_out))
plot(psm_farright$match_out, type = "hist")
summary(psm_farright$lm_model_adj)
print(psm_farright$ATE)

psm_farleft <- perform_psm(data = extremist_df, 
                       balancing_vars = matching_vars, 
                       treatment_var = "farleft",
                       outcome_var = "unique_views_spend")


print(psm_farleft$balancing_tab)
plot(summary(psm_farleft$match_out))
plot(psm_farleft$match_out, type = "hist")
summary(psm_farleft$lm_model_adj)
print(psm_farleft$ATE)


```

## Left-right score

```{r}

formula_lr <- as.formula(str_c("unique_views_spend_log ~ left_right + ", paste(matching_vars, collapse = " + ")))
formula_country_lr <- as.formula(str_c("unique_views_spend_log ~ left_right + ", paste(matching_vars, collapse = " + "), "+ country + positive * populist + negative * populist"))
formula_country_re_lr <- as.formula(str_c("unique_views_spend_log ~ left_right + ", paste(matching_vars, collapse = " + "), "+ (1 | country)"))
formula_country_pop_lr <- as.formula(str_c("unique_views_spend_log ~ left_right + ", paste(matching_vars, collapse = " + "), "+ (populist | country)"))

# Fit linear model
lm_model_lr <- lm(formula_lr, data = extremist_df)
summary(lm_model_lr, robust = TRUE)

# Country fixed effects
lm_country_log <- lm(formula_country_lr, data = extremist_df)
summary(lm_country_log, robust = TRUE)

# Random effects model
# Random intercepts for country
lm_re_lr <- lmer(formula_country_re_lr, data = extremist_df, REML = FALSE)
summary(lm_re_lr)

# Random intercepts and random slopes for populist
lm_re_pop_lr <- lmer(formula_country_pop_lr, data = extremist_df, REML = FALSE)
summary(lm_re_pop_lr)

```

# Perform ipw weighting by country

```{r}

# Perform inverse probability weighting
ipw_out <- map(set_names(countries), ~tryCatch(
  {
    perform_ipw(data = populist_df %>% filter(country == .x), 
                balancing_vars = matching_vars, 
                treatment_var = "populist", 
                outcome_var = "unique_views_spend")
  },
  error = function(e) {
    print(message("Error for country: ", .x, " - ", e$message))
    return(NULL)  # Assigns NULL in case of error
  }
               ))

```

#  Perform propensity score matching by country

```{r}

# Perform propensity score matching with quick method
psm_out <- map(set_names(countries), ~tryCatch(
  {
    perform_psm(data = populist_df %>% filter(country == .x), 
                                       balancing_vars = matching_vars, 
                                       treatment_var = "populist", 
                                       outcome_var = "unique_views_spend",
                                       psm_method = "quick")
    },
  error = function(e) {
    print(message("Error for country: ", .x, " - ", e$message))
    return(NULL)  # Assigns NULL in case of error
  }
               ))


```

# Extract ATEs

```{r}

# Extract ATEs
ATE_psm <- map_dfr(names(psm_out), ~{
  if (!is.null(psm_out[[.x]])) {
    ATE_df <- as_tibble(psm_out[[.x]]$ATE)  # Convert ATE object to a tibble
    ATE_df <- ATE_df %>% mutate(country = .x)  # Add country name as a new column
    return(ATE_df)
  } else {
    NULL  # Empty row with NA for NULL cases
  }
})


ATE_psm %>% select(country, estimate, p.value, conf.low, conf.high)

```

## Visually assess balance

```{r}

# Plot balance
psm_out %>% map(~plot(.x$balancing_tab))




plot(match_out_knn, type = "jitter", interactive = FALSE)
plot(match_out_knn, type = "density", interactive = FALSE)
love.plot(match_out_knn, threshold = 0.1, stars = "std", interactive = FALSE)
plot(summary(match_out_knn))
plot(match_out_knn, type = "hist")


love.plot(match_out_ipw, thresholds = c(m = 0.1))
bal.tab(match_out_ipw)
plot(summary(match_out_ipw))


```

## Compute average treatment effect

```{r}

# Extract matched data
matched_df <- match_data(match_out_knn)

# Compute mean impressions per EUR for matched data
ATE <- matched_df %>%
  filter(!is.na(unique_views_spend)) %>%  # Remove NAs first
  group_by(populist) %>%
  summarize(
    mean_unique_views_spend = mean(unique_views_spend, na.rm = TRUE),
    mean_impressions_spend = mean(impressions_spend, na.rm = TRUE)
  )

print(ATE)

lm_model <- lm(unique_views_spend ~ populist, data = matched_df, weights = matched_df$weights)
summary(lm_model)

formula_adj <- as.formula(str_c("unique_views_spend ~ populist + ", paste(matching_vars, collapse = " + ")))
lm_model_adj <- lm(formula_adj, data = matched_df, weights = matched_df$weights)
summary(lm_model_adj)


lm_ipw <- lm(unique_views_spend ~ populist, data = match_df, weights = match_out_ipw$weights)
summary(lm_ipw)

lm_ipw_adj <- lm(formula_adj, data = match_df, weights = match_out_ipw$weights)
summary(lm_ipw_adj)


```

```{r}
age_controls <- c(
  "targeting_age_distribution_18_24",
  "targeting_age_distribution_25_34",
  "targeting_age_distribution_35_44",
  "targeting_age_distribution_45_54",
  "targeting_age_distribution_55_64",
  "targeting_age_distribution_65"
)

```

```{r}
# ----- Media embeddings as visual content controls -----

embeddings <- read_parquet(str_c(path_data, "ad_library/", "content_embeddings.parquet")) %>%
as_tibble()

id_var <- "id"   # change if your join key has a different name

# Try to detect embedding columns; adjust the pattern if needed
emb_cols <- names(embeddings)[str_detect(names(embeddings), "^(content_embedding_|emb_|media_emb_|dim_)")]

# Fallback: if no naming pattern is found, use all numeric columns except the ID
if (length(emb_cols) == 0) {
  emb_cols <- setdiff(names(embeddings %>% select(where(is.numeric))), id_var)
}

message("Embedding dimensions used: ", length(emb_cols))

# If there are multiple rows per ad (e.g., frames or multiple assets), collapse to one row per ad
embeddings_ad <- embeddings %>%
  group_by(.data[[id_var]]) %>%
  summarise(across(all_of(emb_cols), ~ mean(.x, na.rm = TRUE)), .groups = "drop") %>%
  semi_join(model_df %>% select(all_of(id_var)) %>% distinct(), by = id_var)

# Drop zero-variance dimensions if any
keep_emb_cols <- embeddings_ad %>%
  summarise(across(all_of(emb_cols), ~ sd(.x, na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "term", values_to = "sd") %>%
  filter(!is.na(sd) & sd > 0) %>%
  pull(term)

# PCA on the estimation sample
pca_media <- prcomp(
  embeddings_ad %>% select(all_of(keep_emb_cols)),
  center = TRUE,
  scale. = TRUE
)

# Pre-specify the number of PCs by explained variance
explained_var <- (pca_media$sdev^2) / sum(pca_media$sdev^2)
cum_explained_var <- cumsum(explained_var)
K <- which(cum_explained_var >= 0.80)[1]   # main spec: 80% explained variance

message("Retaining ", K, " PCs (", round(cum_explained_var[K] * 100, 1), "% variance explained)")

media_pcs <- as_tibble(pca_media$x[, seq_len(K), drop = FALSE]) %>%
  setNames(str_c("media_pc_", seq_len(K))) %>%
  mutate(!!id_var := embeddings_ad[[id_var]])

# Join PCs into the regression sample
model_df_media <- model_df %>%
  left_join(media_pcs, by = id_var) %>%
  mutate(
    has_media_embedding = as.integer(!is.na(media_pc_1)),
    across(starts_with("media_pc_"), ~ tidyr::replace_na(.x, 0))
  )

media_covariates <- c(
  "has_media_embedding",
  names(model_df_media %>% select(starts_with("media_pc_")))
)
```
```{r}
#write_parquet(embeddings_ad, sink = "embeddings_ad_smaller.parquet")
colnames(model_df)
```

```{r}
n_distinct(model_df_media$candidate)
```


```{r}
colnames(model_df)
```


```{r}
# Keep original covariates untouched for comparison
covariates_media <- c(covariates, media_covariates)
covariates_media_no_age <- setdiff(covariates_media, age_controls)
print(covariates_media)
print(covariates_media_no_age)
```

```{r}
# Load ad data
embeddings_ad <- read_parquet("../../Code/analysis/embeddings_ad_smaller.parquet") %>% as_tibble()
```



```{r}
# Choose the dependent variable you want to headline
dep_var <- "excess_male_audience"
 #dep_var <- "actual_gender_distribution_unique_views_male"   # current main-code version

#We use only the media covariates

## Populist model with media PCs
formula_populist_media <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media_no_age, collapse = " + "), " + country"
))

lm_populist_media <- lm(formula_populist_media, data = model_df_media)

inference_populist_media <- coeftest(
  lm_populist_media,
  .vcov = vcovCL(lm_populist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

coef_populist_media_no_age <- extract_coef_inference(inference_populist_media)
coef_populist_media_no_age %>% filter(term == "populistPopulist")


## Extremist model with media PCs
formula_extremist_media <- as.formula(str_c(
  dep_var, " ~ extremist + ", paste(covariates_media_no_age, collapse = " + "), " + country"
))

lm_extremist_media <- lm(formula_extremist_media, data = model_df_media)

inference_extremist_media <- coeftest(
  lm_extremist_media,
  .vcov = vcovCL(lm_extremist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

coef_extremist_media_no_age <- extract_coef_inference(inference_extremist_media)
coef_extremist_media_no_age %>% filter(str_detect(term, "extremist"))
coef_extremist_media_no_age 
```
```{r}
# Choose the dependent variable you want to headline
dep_var <- "excess_male_audience"
#dep_var <- "actual_gender_distribution_unique_views_male"   # current main-code version

#We use media and age targeting covariates

## Populist model with media PCs
formula_populist_media <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media, collapse = " + "), " + country"
))

lm_populist_media <- lm(formula_populist_media, data = model_df_media)

inference_populist_media <- coeftest(
  lm_populist_media,
  .vcov = vcovCL(lm_populist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

coef_populist_media <- extract_coef_inference(inference_populist_media)
coef_populist_media %>% filter(term == "populistPopulist")


## Extremist model with media PCs
formula_extremist_media <- as.formula(str_c(
  dep_var, " ~ extremist + ", paste(covariates_media, collapse = " + "), " + country"
))

lm_extremist_media <- lm(formula_extremist_media, data = model_df_media)

inference_extremist_media <- coeftest(
  lm_extremist_media,
  .vcov = vcovCL(lm_extremist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

coef_extremist_media <- extract_coef_inference(inference_extremist_media)
coef_extremist_media %>% filter(str_detect(term, "extremist"))
```


```{r}
summary(lm_populist_media)
```


```{r}
## Extremist
# Predict marginal effects
gge_extremist <- predict_response(model = lm_extremist_media, terms = "extremist", vcov_fun = vcovCL(lm_extremist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE))

# Plot extremist effect
plot_effect_extremist <- ggplot(gge_extremist, aes(x = fct_relevel(x, "Farleft", "Center", "Farright"), y = predicted)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = x), width = 0.1) +
  geom_point(aes(color = x), size = 1.5) +
  scale_color_manual(values = extremist_colors) +
  xlab("") +
  ylab("Share of unique views by men") +
  theme(legend.position = "none")

plot_effect_extremist
ggsave(plot_effect_extremist, filename = str_c(path_figures, "plot_effect_extremist.pdf"), width = 10, height = 10, units = "cm")

## Populist
# Predict marginal effects
gge_populist <- predict_response(lm_populist_media, terms = "populist", vcov_fun = vcovCL(lm_populist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE))

# Plot populist effect
plot_effect_populist <- ggplot(gge_populist, aes(x = x, y = predicted)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = x), width = 0.1) +
  geom_point(aes(color = x), size = 1.5) +
  scale_color_manual(values = populist_colors) +
  xlab("") +
  ylab("Share of unique views by men") +
  theme(legend.position = "none")

plot_effect_populist
ggsave(plot_effect_populist, filename = str_c(path_figures, "plot_effect_populist.pdf"), width = 10, height = 10, units = "cm")

```
```{r}
## Extremist
# Extract coefficients extremist
df_plot <- coef_extremist_media %>% filter(str_detect(term, "extremist")) %>% mutate(term = str_remove(term, "extremist"))

# Plot coefficients extremist
coeff_plot_extremist <- ggplot(data = df_plot, mapping = aes(x = term, y = estimate, fill = term, color = term, shape = term)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low.99, ymax = conf.high.99, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 0.6, size = 0.5) +
  geom_pointrange(aes(ymin = conf.low.95, ymax = conf.high.95, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 1.2, size = 0.5) +
  coord_flip() + labs(x = "", y = "") +
  scale_fill_manual(values = extremist_colors[c(1, 3)]) +
  scale_color_manual(values = extremist_colors[c(1, 3)]) +
  scale_shape_manual(values = c(21, 23)) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 24)) +
  ylab("Coefficient")

coeff_plot_extremist
ggsave(coeff_plot_extremist, filename = str_c(path_figures, "coeff_plot_extremist_cov_.pdf"), width = 10, height = 5, units = "cm")

## Populist
# Extract coefficients populist
df_plot <- coef_populist_media %>% filter(str_detect(term, "populist")) %>% mutate(term = "Populist")

# Plot coefficients populist
coeff_plot_populist <- ggplot(data = df_plot, mapping = aes(x = term, y = estimate, fill = term, color = term)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_pointrange(aes(ymin = conf.low.99, ymax = conf.high.99, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 0.6, size = 0.5, shape = 22) +
  geom_pointrange(aes(ymin = conf.low.95, ymax = conf.high.95, fill = term, color = term),
                  position = position_dodge(width = 0.6), linewidth = 1.2, size = 0.5, shape = 22) +
  coord_flip() + labs(x = "", y = "") +
  scale_fill_manual(values = populist_colors[2]) +
  scale_color_manual(values = populist_colors[2]) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size = 18)) +
  ylab("Coefficient")

coeff_plot_populist
ggsave(coeff_plot_populist, filename = str_c(path_figures, "coeff_plot_populist_cov.pdf"), width = 10, height = 5, units = "cm")
```

```{r}
# Load required libraries
library(tidyverse)
library(broom)
library(lmtest)
library(sandwich)

# 1. Apply cluster-robust standard errors to your existing model
inference_populist_media <- coeftest(
  lm_populist_media, 
  vcov. = vcovCL(lm_populist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

# 2. Extract coefficients and 95% confidence intervals into a clean dataframe
coef_df <- tidy(inference_populist_media, conf.int = TRUE, conf.level = 0.95)

# 3. Filter for the specific variables we want in Table 1 and clean up their names
plot_data <- coef_df %>%
  filter(term %in% c("populistPopulist", "platformFacebook", "platformInstagram", 
                     "party_ad", "sentimentPositive", "sentimentNegative")) %>%
  mutate(
    # Create clean, readable labels for the Y-axis
    clean_term = case_when(
      term == "populistPopulist" ~ "Populist",
      term == "platformFacebook" ~ "Facebook",
      term == "platformInstagram" ~ "Instagram",
      term == "party_ad" ~ "Party Ad",
      term == "sentimentPositive" ~ "Positive Sentiment",
      term == "sentimentNegative" ~ "Negative Sentiment"
    ),
    # Reorder the terms so they appear in a logical top-to-bottom order on the plot
    clean_term = factor(clean_term, levels = rev(c("Populist", "Facebook", "Instagram", 
                                                   "Party Ad", "Positive Sentiment", "Negative Sentiment")))
  )

# 4. Generate the dynamic coefficient plot
table1_coef_plot <- ggplot(plot_data, aes(x = estimate, y = clean_term)) +
  # Add a vertical dashed line at zero (null effect)
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  
  # Add the point estimates and confidence interval whiskers
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high), 
                  color = "darkblue", fill = "darkblue", shape = 21, size = 0.8, linewidth = 1) +
  
  # Clean up labels and titles
  labs(
    x = "Effect on Excess Share of Male Audience",
    y = NULL,
    
  ) +
  #caption = "Error bars represent 95% cluster-robust confidence intervals."
  # Apply a clean academic theme
  theme_bw() +
  theme(
    text = element_text(size = 14),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(color = "black", size = 12),
    axis.text.x = element_text(color = "black", size = 12)
  )

# 5. View the plot
print(table1_coef_plot)

# Optional: Save it straight to your figures directory
ggsave("../../Doc/Nat Hum Behav/figures/table1_coef_plot.pdf", table1_coef_plot, width = 18, height = 10, units = "cm")
```



```{r}
#model_df_media %>% count(target_ages)
library(dplyr)
library(tidyr)

model_df <- model_df %>%
  separate(target_ages,
           into = c("age_min", "age_max"),
           sep = ",",
           convert = TRUE)
```

```{r}
model_df <- model_df %>%
  mutate(
    targ_18_24 = age_min <= 24 & age_max >= 18,
    targ_25_34 = age_min <= 34 & age_max >= 25,
    targ_35_44 = age_min <= 44 & age_max >= 35,
    targ_45_54 = age_min <= 54 & age_max >= 45,
    targ_55_64 = age_min <= 64 & age_max >= 55,
    targ_65_plus = age_max >= 65
  )

model_df_media <- model_df_media %>%
  mutate(across(starts_with("targ_"), as.integer))
```

```{r}
library(dplyr)

# Calculate the average excess male share for non-populist ads
non_populist_stat <- model_df %>%
  filter(populist == "Non-populist") %>%
  summarize(
    mean_excess_male = mean(excess_male_audience, na.rm = TRUE)
  )

# Extract and format the number as a percentage for the manuscript
formatted_X <- paste0(round(non_populist_stat$mean_excess_male * 100, 1), "%")

print(formatted_X)
```


```{r}
age_controls <- c(
  "targ_18_24",
  "targ_25_34",
  "targ_35_44",
  "targ_45_54",
  "targ_55_64",
  "targ_65_plus"
)

covariates_media <- c(covariates_media, age_controls)

#model_df %>%
  #summarise(across(starts_with("targ_"), mean))

```

```{r}
print(covariates_media)
#colnames(model_df)

```

```{r}
colnames(model_df_media)
```


```{r}
library(dplyr)

results_plot <- bind_rows(
  coef_populist_media %>%
    filter(term == "populistPopulist") %>%
    mutate(model = "Media + Age"),

  coef_populist_media_no_age %>%
    filter(term == "populistPopulist") %>%
    mutate(model = "Media only")
)
```


```{r}
library(ggplot2)

ggplot(results_plot, aes(x = model, y = estimate)) +
  geom_point(size = 3) +
  geom_errorbar(aes(
    ymin = estimate - 1.96 * std.error,
    ymax = estimate + 1.96 * std.error
  ), width = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(
    x = "",
    y = "Effect on male audience share",
    title = "Effect of Populist Ads on Gender Targeting",
    subtitle = "Estimates with and without age targeting controls"
  ) +
  theme_minimal()
```

```{r}
library(dplyr)
library(stringr)

results_extreme <- bind_rows(
  
  # WITH media + age
  coef_extremist_media %>%
    filter(str_detect(term, "extremist")) %>%
    mutate(model = "Media + Age"),
  
  # WITH media, NO age
  coef_extremist_media_no_age %>%
    filter(str_detect(term, "extremist")) %>%
    mutate(model = "Media only")
)
```


```{r}
results_extreme <- results_extreme %>%
  mutate(
    ideology = case_when(
      str_detect(term, "left") ~ "Far-left",
      str_detect(term, "right") ~ "Far-right",
      TRUE ~ term
    )
  )
```

```{r}
library(ggplot2)

ggplot(results_extreme,
       aes(x = ideology, y = estimate, color = model)) +
  
  geom_point(position = position_dodge(width = 0.4), size = 3) +
  
  geom_errorbar(
    aes(
      ymin = estimate - 1.96 * std.error,
      ymax = estimate + 1.96 * std.error
    ),
    position = position_dodge(width = 0.4),
    width = 0.1
  ) +
  
  geom_hline(yintercept = 0, linetype = "dashed") +
  
  labs(
    x = "",
    y = "Effect on male audience share",
    color = "",
    title = "Extremist Effects on Gender Targeting",
    subtitle = "With and without age targeting controls"
  ) +
  
  theme_minimal()
```

print(vars_needed)

```{r}

library(clubSandwich)
# Choose the dependent variable you want to headline
dep_var <- "excess_male_audience"
# dep_var <- "actual_gender_distribution_unique_views_male"   # current main-code version

#We use only the media covariates

vars_needed <- c(
  dep_var,
  "populist",
  covariates_media,
  "country",
  "national_party"
)

model_df_media_pop <- model_df_media %>%
  dplyr::select(all_of(vars_needed)) %>%
  na.omit()

## Populist model with media PCs
formula_populist_media_random <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media_no_age, collapse = " + "), " + (1 | country)"
))

lm_populist_media_random <- lmer(formula_populist_media_random, data = model_df_media,REML = FALSE)

# inference_populist_media_random <- coef_test(
#   lm_populist_media_random,
#   vcov = "CR2",
#   cluster = model_df_media_pop$national_party
# )

summary(lm_populist_media_random)

#coef_populist_media_no_age_random <- extract_coef_inference(lm_populist_media_random)
#coef_populist_media_no_age_random %>% filter(term == "populistPopulist")



## Extremist model with media PCs
formula_extremist_media_random <- as.formula(str_c(
  dep_var, " ~ extremist + ", paste(covariates_media_no_age, collapse = " + "), " +(1 | country)"
))

lm_extremist_media_random <- lmer(formula_extremist_media_random, data = model_df_media,REML = FALSE)

summary(lm_extremist_media_random)

# coef_extremist_media_no_age_random <- extract_coef_inference(inference_extremist_media_random)
# coef_extremist_media_no_age_random %>% filter(str_detect(term, "extremist"))
# coef_extremist_media_no_age_random 
```

```{r}
library(clubSandwich)
# Choose the dependent variable you want to headline
dep_var <- "excess_male_audience"
# dep_var <- "actual_gender_distribution_unique_views_male"   # current main-code version

#We use only the media covariates

vars_needed <- c(
  dep_var,
  "populist",
  covariates_media_no_age,
  "country",
  "national_party"
)

# model_df_media_pop <- model_df_media %>%
#   dplyr::select(all_of(vars_needed)) %>%
#   na.omit()

## Populist model with media PCs
formula_populist_media_random_age <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media, collapse = " + "), " + (1 | country)"
))

lm_populist_media_random_age <- lmer(formula_populist_media_random_age, data = model_df_media,REML = FALSE)

# inference_populist_media_random <- coef_test(
#   lm_populist_media_random,
#   vcov = "CR2",
#   cluster = model_df_media_pop$national_party
# )

summary(lm_populist_media_random_age)
#coef_populist_media_no_age_random <- extract_coef_inference(lm_populist_media_random)
#coef_populist_media_no_age_random %>% filter(term == "populistPopulist")



## Extremist model with media PCs
formula_extremist_media_random_age <- as.formula(str_c(
  dep_var, " ~ extremist + ", paste(covariates_media, collapse = " + "), " +(1 | country)"
))

lm_extremist_media_random_age <- lmer(formula_extremist_media_random_age, data = model_df_media,REML = FALSE)

summary(lm_extremist_media_random_age)

# coef_extremist_media_no_age_random <- extract_coef_inference(inference_extremist_media_random)
# coef_extremist_media_no_age_random %>% filter(str_detect(term, "extremist"))
# coef_extremist_media_no_age_random 
```

```{r}

## Extremist
# Create formula
formula_extremist_dep <- as.formula(str_c("actual_gender_distribution_unique_views_male" , " ~ ", "extremist", " + ", paste(c(covariates_media), collapse = " + "), " + country"))

# Estimate linear model
lm_extremist_dep <- lm(formula = formula_extremist_dep, data = model_df_media)

# Inference
inferece_extremist_dep <- coeftest(lm_extremist_dep, .vcov = vcovCL(lm_extremist_dep, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_extremist_dep <- extract_coef_inference(inferece_extremist_dep)
coef_extremist_dep

## Populist
# Create formula
formula_populist_dep <- as.formula(str_c("actual_gender_distribution_unique_views_male" , " ~ ", "populist", " + ", paste(c(covariates_media), collapse = " + "), " + country"))

# Estimate linear model
lm_populist_dep <- lm(formula = formula_populist_dep, data = model_df_media)

# Inference
inferece_populist_dep <- coeftest(lm_populist_dep, vcov = vcovCL(lm_populist_dep, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_populist_dep <- extract_coef_inference(inferece_populist_dep)
coef_populist_dep

```
# Robustness check: Include share of male users per country - done

```{r}
#Note: We need to exclude country fixed effects for this analysis to avoid multicollinearity

## Extremist
# Create formula
formula_extremist_male <- as.formula(str_c("excess_male_audience" , " ~ ", "extremist", " + ", paste(c(covariates_media, male_share_country), collapse = " + ")))

# Estimate linear model
lm_extremist_male <- lm(formula = formula_extremist_male, data = model_df_media)

# Inference
inference_extremist_male <- coeftest(lm_extremist_male, .vcov = vcovCL(lm_extremist_male, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_extremist_male <- extract_coef_inference(inference_extremist_male)
coef_extremist_male

## Populist
# Create formula
formula_populist_male <- as.formula(str_c("excess_male_audience" , " ~ ", "populist", " + ", paste(c(covariates_media, male_share_country), collapse = " + ")))

# Estimate linear model
lm_populist_male <- lm(formula = formula_populist_male, data = model_df_media)

# Inference
inference_populist_male <- coeftest(lm_populist_male, .vcov = vcovCL(lm_populist_male, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
coef_populist_male <- extract_coef_inference(inference_populist_male)
coef_populist_male

# Results: Coefficients are consistent with main analysis
# => positive and significant coefficient for farright; negative and significant coefficient for farleft
# => positive and significant coefficient for populist
```

```{r}
# 1. Extract all the variable names used in your regression formula
vars_in_model <- all.vars(formula_populist_media)

# 2. Count the number of unique values for each of those variables in the filtered data
unique_counts <- sapply(model_df_2_months[vars_in_model], function(x) length(unique(na.omit(x))))

# 3. Print out ONLY the variables that are causing the crash (less than 2 unique values)
unique_counts[unique_counts < 2]
```


#Data subset - done
```{r}
# Define the start of the election
election_date <- as.Date("2024-06-09")

# --- 1. Data Sample Restriction: Final Two Months ---
model_df_2_months <- model_df_media %>%
  filter(ad_creation_time >= (election_date - months(2)))

# Re-estimate the model
lm_populist_2m <- lm(formula_populist_media, data = model_df_2_months)
inference_populist_2m <- coeftest(lm_populist_2m, .vcov = vcovCL(lm_populist_2m, cluster = ~ national_party, type = "HC1", cadjust = TRUE))

# Extract the coefficient of interest
coef_populist_2m <- extract_coef_inference(inference_populist_2m)
coef_populist_2m %>% filter(term == "populistPopulist")


# --- 2. Data Sample Restriction: Final One Month ---
model_df_1_month <- model_df_media %>%
  filter(ad_creation_time >= (election_date - months(1)))

# Re-estimate the model
lm_populist_1m <- lm(formula_populist_media, data = model_df_1_month)
inference_populist_1m <- coeftest(lm_populist_1m, .vcov = vcovCL(lm_populist_1m, cluster = ~ national_party, type = "HC1", cadjust = TRUE))

# Extract the coefficient of interest
coef_populist_1m <- extract_coef_inference(inference_populist_1m)
coef_populist_1m %>% filter(term == "populistPopulist")
```


```{r}
# 1. Define the formula with the interaction term (populist * extremist)
formula_interaction <- as.formula(
  str_c("excess_male_audience ~ populist * extremist + ", 
        paste(covariates_media, collapse = " + "), 
        " + country")
)

# 2. Fit the linear model
lm_interaction <- lm(formula_interaction, data = model_df_media)

# 3. Apply cluster-robust standard errors (clustered by national party)
library(lmtest)
library(sandwich)
library(broom)

inference_interaction <- coeftest(
  lm_interaction, 
  vcov. = vcovCL(lm_interaction, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

# 4. Extract and view the coefficients, focusing specifically on the interaction terms
coef_interaction_df <- tidy(inference_interaction, conf.int = TRUE, conf.level = 0.95)

# Filter to show the main effects and the interaction effects
coef_interaction_df %>% 
  filter(grepl("populist|extremist", term)) %>%
  select(term, estimate, std.error, p.value, conf.low, conf.high)
```

```{r}
library(dplyr)

# Group by media_type and count the number of ads
media_type_summary <- embeddings %>%
  group_by(content_type) %>%
  summarize(
    total_embeddings = n(),             # Counts every row
    unique_ads = n_distinct(id)         # Counts unique ad IDs only
  ) %>%
  arrange(desc(unique_ads))             # Sorts from most to least common

# Print the result
print(media_type_summary)
```

```{r}
library(dplyr)
library(broom)
library(lmtest)
library(sandwich)
library(ggplot2)
library(forcats)

# 1. Setup the covariate blocks using your existing variables
dep_var <- "excess_male_audience"

# We use setdiff() to remove age controls from your existing 'covariates'
covariates_base <- setdiff(covariates, age_controls)

# Your script already defined these two:
# covariates_media <- c(covariates, media_covariates)
# covariates_media_no_age <- setdiff(covariates_media, age_controls)

# 2. Define the four ablation formulas
formula_base <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_base, collapse = " + "), " + country"
))

formula_age <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates, collapse = " + "), " + country"
))

formula_media <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media_no_age, collapse = " + "), " + country"
))

formula_full <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media, collapse = " + "), " + country"
))

# 3. Fit the models (using model_df_media)
lm_base  <- lm(formula_base, data = model_df_media)
lm_age   <- lm(formula_age, data = model_df_media)
lm_media <- lm(formula_media, data = model_df_media)
lm_full  <- lm(formula_full, data = model_df_media)

# 4. Helper function to extract cluster-robust standard errors
extract_populist_coef <- function(model, model_name) {
  inference <- coeftest(model, vcov. = vcovCL(model, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
  coef_df <- tidy(inference, conf.int = TRUE, conf.level = 0.95)
  
  coef_df %>%
    filter(term == "populistPopulist") %>%
    mutate(model_spec = model_name)
}

# 5. Extract and bind the results together
ablation_results <- bind_rows(
  extract_populist_coef(lm_base, "1. Base Controls Only"),
  extract_populist_coef(lm_media, "2. Base + Media (No Age)"),
  extract_populist_coef(lm_age, "3. Base + Age (No Media)"),
  extract_populist_coef(lm_full, "4. Full Model (Base + Age + Media)")
)

# Print the results to console
print(ablation_results %>% select(model_spec, estimate, std.error, p.value, conf.low, conf.high))

# 6. Plot the Ablation Study Results
ablation_plot <- ggplot(ablation_results, aes(x = estimate, y = fct_rev(model_spec))) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high), 
                  color = "darkred", fill = "darkred", shape = 21, size = 1, linewidth = 1.2) +
  labs(
    title = "Covariate Ablation: Effect of Populism on Male Audience Share",
    subtitle = "Comparing model specifications with and without age/media controls",
    x = "Estimated Effect on Excess Male Share",
    y = NULL
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 14),
    axis.text.y = element_text(color = "black", size = 12, face = "bold")
  )

print(ablation_plot)
```
```{r}
# Check if the generated "Age" formula matches your main baseline formula
formula_age == formula_populist

# Check if the generated "Full" formula matches your main media formula
formula_full == formula_populist_media
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

df_extremist_gender <- model_df %>%
  filter(
    !is.na(country),
    !is.na(extremist),
    !is.na(actual_gender_distribution_unique_views_female),
    !is.na(actual_gender_distribution_unique_views_male)
  ) %>%
  mutate(
    extremist = factor(extremist, levels = c("Center", "Farleft", "Farright"))
  ) %>%
  group_by(country, extremist) %>%
  summarize(
    Female = mean(actual_gender_distribution_unique_views_female, na.rm = TRUE),
    Male   = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = c(Female, Male),
    names_to = "gender",
    values_to = "share"
  ) %>%
  mutate(
    gender = factor(gender, levels = c("Female", "Male")),
    country = factor(country, levels = sort(unique(country), decreasing = TRUE))
  ) %>%
  complete(
    country,
    extremist = factor(c("Center", "Farleft", "Farright"),
                       levels = c("Center", "Farleft", "Farright")),
    gender = factor(c("Female", "Male"), levels = c("Female", "Male")),
    fill = list(share = NA_real_)
  )

extremist_colors <- c(
  "Center" = "grey",
  "Farleft" = "#C44E7F",
  "Farright" = "#2B6CB0"
)

plot_extremist_gender_bar <- ggplot(
  df_extremist_gender,
  aes(
    x = share,
    y = country,
    fill = extremist,
    group = extremist
  )
) +
  geom_col(
    position = position_dodge2(
      width = 1,
      preserve = "single",
      padding = 0
    ),
    width = 1,
    na.rm = TRUE
  ) +
  geom_text(
    aes(label =  ""),
    position = position_dodge2(
      width = 0.40,
      preserve = "single",
      padding = 0
    ),
    hjust = 1.05,
    size = 2.4,
    color = "black",
    na.rm = TRUE
  ) +
  facet_wrap(~ gender, nrow = 1) +
  scale_fill_manual(
    values = extremist_colors,
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(0, 0.8),
    breaks = seq(0, 0.8, by = 0.2),
    labels = number_format(accuracy = 0.1)
  ) +
  labs(
    x = "Share of unique views by gender",
    y = NULL,
    fill = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(fill = "grey80", color = "grey40"),
    strip.text = element_text(size = 9),
    axis.text.y = element_text(size = 9),
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(size = 9),
    legend.text = element_text(size = 9),
    legend.key.size = unit(0.45, "cm")
  )

plot_extremist_gender_bar

ggsave(
  filename = file.path(path_figures, "bar_share_views_by_gender_extremist.pdf"),
  plot = plot_extremist_gender_bar,
  width = 8,
  height = 6,
  device = cairo_pdf
)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

df_extremist_gender <- model_df %>%
  filter(
    !is.na(country),
    !is.na(extremist),
    !is.na(actual_gender_distribution_unique_views_female),
    !is.na(actual_gender_distribution_unique_views_male)
  ) %>%
  mutate(
    extremist = factor(extremist, levels = c("Center", "Farleft", "Farright"))
  ) %>%
  group_by(country, extremist) %>%
  summarize(
    Female = mean(actual_gender_distribution_unique_views_female, na.rm = TRUE),
    Male   = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = c(Female, Male),
    names_to = "gender",
    values_to = "share"
  ) %>%
  mutate(
    gender = factor(gender, levels = c("Female", "Male")),
    country = factor(country, levels = sort(unique(country), decreasing = TRUE))
  ) %>%
  complete(
    country,
    extremist = factor(c("Center", "Farleft", "Farright"),
                       levels = c("Center", "Farleft", "Farright")),
    gender = factor(c("Female", "Male"), levels = c("Female", "Male")),
    fill = list(share = NA_real_)
  )

# --------------------------------------------------
# Add numeric y-positions to control spacing manually
# --------------------------------------------------

country_levels <- levels(df_extremist_gender$country)

country_gap <- 3.1   # increase this for more space between countries
bar_offset  <- 0.8   # vertical distance between bars within the same country
bar_width   <- 0.75   # thickness of each bar

df_extremist_gender <- df_extremist_gender %>%
  mutate(
    country_id = as.numeric(country) * country_gap,
    extremist_offset = case_when(
      extremist == "Center"   ~ -bar_offset,
      extremist == "Farleft"  ~ 0,
      extremist == "Farright" ~  bar_offset
    ),
    y_pos = country_id + extremist_offset
  )

extremist_colors <- c(
  "Center" = "grey",
  "Farleft" = "#C44E7F",
  "Farright" = "#2B6CB0"
)

plot_extremist_gender_bar <- ggplot(
  df_extremist_gender,
  aes(
    x = share,
    y = y_pos,
    fill = extremist
  )
) +
  geom_col(
    width = bar_width,
    orientation = "y",
    na.rm = TRUE
  ) +
  geom_text(
    aes(label = ""),
    hjust = 1.05,
    size = 2.4,
    color = "black",
    na.rm = TRUE
  ) +
  facet_wrap(~ gender, nrow = 1) +
  scale_fill_manual(
    values = extremist_colors,
    drop = FALSE
  ) +
  scale_x_continuous(
    limits = c(0, 0.8),
    breaks = seq(0, 0.8, by = 0.2),
    labels = number_format(accuracy = 0.1)
  ) +
  scale_y_continuous(
    breaks = seq_along(country_levels) * country_gap,
    labels = country_levels,
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    x = "Share of unique views by gender",
    y = NULL,
    fill = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(fill = "grey80", color = "grey40"),
    strip.text = element_text(size = 9),
    axis.text.y = element_text(size = 9),
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(size = 9),
    legend.text = element_text(size = 9),
    legend.key.size = unit(0.45, "cm")
  )

plot_extremist_gender_bar

ggsave(
  filename = file.path(path_figures, "bar_share_views_by_gender_extremist.pdf"),
  plot = plot_extremist_gender_bar,
  width = 8,
  height = 8,
  device = cairo_pdf
)
```

```{r}
#install.packages("car")
library(car)
calculate_vif_controls <- function(data,
                                   controls = covariates,
                                   include_country = TRUE) {
  
  # Build formula using only controls
  rhs_vars <- controls
  
  if (include_country) {
    rhs_vars <- c(rhs_vars, "country")
  }
  
  vif_formula <- as.formula(
    str_c("actual_gender_distribution_unique_views_male ~ ",
          paste(rhs_vars, collapse = " + "))
  )
  
  # Estimate auxiliary linear model for VIF calculation
  vif_model <- lm(
    formula = vif_formula,
    data = data
  )
  
  # Calculate VIFs
  vif_values <- car::vif(vif_model)
  
  # Convert output to tidy dataframe
  if (is.matrix(vif_values)) {
    vif_df <- as.data.frame(vif_values) %>%
      rownames_to_column("term") %>%
      mutate(
        VIF_adjusted = GVIF^(1 / (2 * Df))
      ) %>%
      arrange(desc(VIF_adjusted))
  } else {
    vif_df <- tibble(
      term = names(vif_values),
      VIF = as.numeric(vif_values)
    ) %>%
      arrange(desc(VIF))
  }
  
  return(vif_df)
}

vif_controls <- calculate_vif_controls(
  data = model_df_media,
  controls = covariates_media,
  include_country = TRUE
)

vif_controls
```

