

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# File description

```{r}
# - Descriptive analysis for populist vs. non-populist ads (Figure 1)
# - Main regression and marginal effect for populist ads (Figures 2 and 3)
# - Descriptive analysis for far-left / center / far-right ads (Figure 4)
# - Extremism regression (Figure 5)
# - Supplement B robustness checks
# - Supplement C interaction between populism and political extremism
```

# Set up environment

```{r, include=FALSE}
# Clean environment
rm(list = ls())

# Load packages
library(arrow)
library(tidyverse)
library(lubridate)
library(ggrepel)
library(MatchIt)
library(WeightIt)
library(cobalt)
library(marginaleffects)
library(lme4)
library(broom)
library(sandwich)
library(clubSandwich)
library(lmtest)
library(ggpattern)
library(ggeffects)
library(sf)
library(grid)

# Load helpers used in the original project
if (file.exists("utils.R")) {
  source("utils.R")
}

# Fallback for a helper that is used throughout the original analysis file
if (!exists("extract_coef_inference")) {
  extract_coef_inference <- function(inference_obj) {
    coef_df <- broom::tidy(inference_obj)
    coef_df %>%
      mutate(
        conf.low.95 = estimate - qnorm(0.975) * std.error,
        conf.high.95 = estimate + qnorm(0.975) * std.error,
        conf.low.99 = estimate - qnorm(0.995) * std.error,
        conf.high.99 = estimate + qnorm(0.995) * std.error
      )
  }
}

if (!exists("perform_psm")) {
  stop("perform_psm() is expected from utils.R for Supplement B.4.")
}

# Set seed
set.seed(42)

# Define paths to data and output
path_data <- "../../Data/"
path_figures <- "../../Doc/Nat Hum Behav/figures/"
dir.create(path_figures, recursive = TRUE, showWarnings = FALSE)
```

# Graph theme setup

```{r}
theme_set(
  theme_bw() +
    theme(
      legend.position = c(0.7, 0.9),
      legend.title = element_blank(),
      legend.direction = "horizontal",
      legend.text = element_text(colour = "black", size = 12),
      legend.background = element_rect(fill = "transparent", colour = NA),
      legend.key = element_rect(fill = "transparent", colour = "transparent"),
      legend.key.width = unit(0.5, "cm"),
      legend.key.height = unit(0.5, "cm"),
      axis.text.x = element_text(colour = "black", size = 12, vjust = 0.5),
      axis.text.y = element_text(colour = "black", size = 12, vjust = 0.5),
      axis.title.x = element_text(size = 12),
      axis.title.y = element_text(size = 12, vjust = 1.5)
    )
)

# Color mappings used in the original script
extremist_colors <- c("darkred", "darkgreen", "darkblue")
populist_colors <- c("darkcyan", "darkorange")
```

# Load and prepare data

```{r}
# Load ad data
ad_data <- read_parquet(str_c(path_data, "ad_library/", "EU_2024_ad_library_preprocessed.parquet")) %>%
  as_tibble()

# Unnest targeting and observed-audience columns
ad_data <- ad_data %>%
  unnest_wider(targeting_gender_distribution, names_sep = "_") %>%
  unnest_wider(targeting_age_distribution, names_sep = "_") %>%
  unnest_wider(actual_gender_distribution_unique_views, names_sep = "_") %>%
  unnest_wider(actual_age_distribution_unique_views, names_sep = "_")

ad_data <- ad_data %>%
  rename_with(~ str_replace_all(., "-", "_"), matches("targeting_age_distribution|actual_age_distribution_unique_views")) %>%
  rename_with(~ str_replace_all(., "\\+", ""), matches("targeting_age_distribution|actual_age_distribution_unique_views"))

# Vector of countries
countries <- ad_data %>%
  distinct(country) %>%
  pull(country)

# Define covariates from the original script
ad_vars <- c(
  "platform",
  "ad_duration_scaled",
  "n_active_ads_country_scaled",
  "party_ad",
  "sentiment",
  "weekday_start",
  "weekday_end"
)

targeting <- ad_data %>%
  select(contains("targeting_age_distribution") & !contains("13_17")) %>%
  colnames()

male_share_country <- c("FB_male_total_country", "IG_male_total_country")

covariates <- c(ad_vars, targeting)

# Prepare analysis sample
model_df <- ad_data %>%
  filter(eu_parliament_2024 == 1) %>%
  filter(target_gender == "All") %>%
  mutate(
    excess_male_audience = actual_gender_distribution_unique_views_male - actual_gender_distribution_unique_views_female,
    populist = as.integer(ifelse(is.na(populist), 0, populist)),
    populist = factor(populist, levels = c(0, 1), labels = c("Non-populist", "Populist")),
    farright = as.integer(ifelse(is.na(farright), 0, farright)),
    farleft = as.integer(ifelse(is.na(farleft), 0, farleft)),
    extremist = ifelse(farright == 1, "Farright", ifelse(farleft == 1, "Farleft", "Center")),
    extremist = factor(extremist, levels = c("Center", "Farleft", "Farright"), labels = c("Center", "Farleft", "Farright")),
    platform = factor(platform, levels = c("FB_IG", "FB", "IG"), labels = c("Facebook and Instagram", "Facebook", "Instagram")),
    sentiment = factor(sentiment, levels = c("neutral", "positive", "negative"), labels = c("Neutral", "Positive", "Negative")),
    across(.cols = c(weekday_start, weekday_end), ~ as_factor(.x)),
    across(.cols = c(n_active_ads_country, ad_duration, spend), ~ scale(.x) %>% as.vector(), .names = "{.col}_scaled")
  )
```

# Descriptive statistics reported in the paper

```{r}
# Overlap between populist and extremist classifications
model_df %>%
  filter(populist == "Populist" & extremist %in% c("Farleft", "Farright")) %>%
  nrow()

model_df %>%
  filter(populist == "Populist") %>%
  group_by(extremist) %>%
  summarize(n = n(), .groups = "drop")

# Share of populist ads in the estimation sample
model_df %>%
  group_by(populist) %>%
  summarize(share_ads = n() / nrow(model_df), .groups = "drop")

# Overall male / female audience shares
model_df %>%
  summarize(
    male_share = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE),
    female_share = mean(actual_gender_distribution_unique_views_female, na.rm = TRUE)
  )

# Average excess male share for non-populist ads
model_df %>%
  filter(populist == "Non-populist") %>%
  summarize(mean_excess_male = mean(excess_male_audience, na.rm = TRUE))
```

# Figure 1: Populist vs. non-populist descriptive analysis

## Figure 1a: Country-level difference in male audience share

```{r}
fig1a_df <- model_df %>%
  group_by(country, populist) %>%
  summarize(
    male_share = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(names_from = populist, values_from = male_share) %>%
  mutate(
    diff = Populist - `Non-populist`,
    direction = case_when(
      is.na(Populist) ~ "No populist ads",
      diff >= 0 ~ "Populist > Non-populist",
      TRUE ~ "Populist < Non-populist"
    ),
    label_diff = case_when(
      is.na(diff) ~ NA_character_,
      TRUE ~ sprintf("%+.1f%%", diff * 100)
    )
  ) %>%
  arrange(desc(coalesce(Populist, `Non-populist`))) %>%
  mutate(country = factor(country, levels = rev(country)))

fig1a_plot <- ggplot(fig1a_df, aes(y = country)) +
  geom_segment(
    data = fig1a_df %>% filter(direction != "No populist ads"),
    aes(
      x = `Non-populist`,
      xend = Populist,
      yend = country,
      color = direction
    ),
    linewidth = 0.9,
    arrow = grid::arrow(length = grid::unit(0.10, "inches"), type = "closed")
  ) +
  geom_point(
    aes(x = `Non-populist`, color = direction),
    size = 1.8
  ) +
  geom_text(
    data = fig1a_df %>% filter(direction != "No populist ads"),
    aes(x = pmax(`Non-populist`, Populist) + 0.012, label = label_diff, color = direction),
    hjust = 0,
    size = 3
  ) +
  scale_color_manual(
    values = c(
      "Populist > Non-populist" = "#2B6CB0",
      "Populist < Non-populist" = "#C44E52",
      "No populist ads" = "black"
    )
  ) +
  scale_x_continuous(
    limits = c(0.40, 0.72),
    breaks = seq(0.40, 0.70, by = 0.05),
    labels = scales::percent_format(accuracy = 1),
    expand = expansion(mult = c(0.01, 0.10))
  ) +
  labs(
    x = "Share of unique views by male users",
    y = NULL,
    color = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = c(0.82, 0.15),
    legend.background = element_rect(fill = "transparent", colour = NA),
    panel.grid.minor = element_blank()
  )

fig1a_plot

ggsave(
  filename = file.path(path_figures, "figure1a_populist_country_difference.pdf"),
  plot = fig1a_plot,
  width = 8,
  height = 6,
  device = cairo_pdf
)
```

## Map data

```{r}
map_data <- read_sf(dsn = str_c(path_data, "misc/world_shape_files/ne_10m_admin_0_countries.shp")) %>%
  st_as_sf()

# Handle Cyprus explicitly, mirroring the original script
cyprus_geometry <- map_data %>%
  filter(str_detect(NAME, "Cyprus")) %>%
  mutate(ISO_A2_EH = "CY") %>%
  group_by(ISO_A2_EH) %>%
  summarise() %>%
  st_geometry()

eu <- map_data %>%
  filter(ISO_A2_EH %in% countries, TYPE %in% c("Country", "Sovereign country")) %>%
  select(ISO_A2_EH, geometry) %>%
  mutate(
    geometry = case_when(
      ISO_A2_EH == "CY" ~ cyprus_geometry,
      TRUE ~ geometry
    ),
    pattern = case_when(
      ISO_A2_EH %in% c("PT", "FR") ~ "crosshatch",
      TRUE ~ "stripe"
    )
  )

lambert_crs <- 3035
xlim_europe <- c(2500000, 6500000)
ylim_europe <- c(1050000, 5300000)

map_base <- ggplot() +
  geom_sf(data = map_data, aes(geometry = geometry), fill = "lightgrey", color = "white", size = 0.1) +
  geom_sf_pattern(
    data = eu %>% filter(!(ISO_A2_EH %in% c("FR", "PT"))),
    aes(geometry = geometry, pattern = pattern, pattern_fill = pattern, fill = pattern),
    pattern_density = 0.2,
    pattern_spacing = 0.03,
    pattern_angle = 45,
    pattern_color = "black",
    fill = "lightgrey",
    color = "white",
    size = 0.1
  ) +
  geom_sf_pattern(
    data = eu %>% filter(ISO_A2_EH %in% c("FR", "PT")),
    aes(geometry = geometry, pattern = pattern, pattern_fill = pattern),
    pattern_density = 0.5,
    pattern_spacing = 0.03,
    pattern_angle = 90,
    pattern_color = "darkred",
    fill = "lightgrey",
    color = "white",
    size = 0.1
  ) +
  scale_pattern_manual(values = c("stripe" = "stripe", "crosshatch" = "stripe"), labels = c("Ads prohibited", "No data")) +
  scale_pattern_fill_manual(values = c("stripe" = "black", "crosshatch" = "darkred"), labels = c("Ads prohibited", "No data")) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    axis.text.y = element_blank(),
    axis.text.x = element_blank(),
    legend.spacing.y = unit(0.1, "cm"),
    legend.box = "vertical",
    legend.box.spacing = unit(0.5, "cm")
  )
```

## Figure 1b: Populist vs. non-populist excess male share map

```{r}
fig1b_df <- model_df %>%
  group_by(country, populist) %>%
  summarize(
    excess_male_audience = mean(excess_male_audience, na.rm = TRUE),
    actual_gender_distribution_unique_views_male = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  right_join(eu, by = c("country" = "ISO_A2_EH")) %>%
  mutate(populist = forcats::fct_relevel(populist, "Non-populist", "Populist")) %>%
  drop_na(populist) %>%
  st_as_sf()

map_populist_excess_male <- map_base +
  geom_sf(data = fig1b_df, aes(geometry = geometry, fill = excess_male_audience), color = "white", size = 0.1) +
  coord_sf(crs = lambert_crs, xlim = xlim_europe, ylim = ylim_europe) +
  scale_fill_gradient2(
    low = "darkred",
    mid = "white",
    high = "darkblue",
    midpoint = 0,
    limits = c(-0.25, 0.45),
    breaks = seq(-0.2, 0.4, 0.2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  facet_wrap(~ populist, nrow = 1, ncol = 2) +
  guides(
    fill = guide_colorbar(barwidth = unit(10, "cm"), barheight = unit(0.5, "cm"), order = 1)
  )

map_populist_excess_male

ggsave(
  filename = str_c(path_figures, "map_excess_views_male_populist.svg"),
  plot = map_populist_excess_male,
  width = 20,
  height = 10,
  units = "cm"
)
```

# Media embeddings as visual content controls

```{r}
embeddings <- read_parquet(str_c(path_data, "ad_library/", "content_embeddings.parquet")) %>%
  as_tibble()

id_var <- "id"

emb_cols <- names(embeddings)[str_detect(names(embeddings), "^(content_embedding_|emb_|media_emb_|dim_)")]
if (length(emb_cols) == 0) {
  emb_cols <- setdiff(names(embeddings %>% select(where(is.numeric))), id_var)
}

message("Embedding dimensions used: ", length(emb_cols))

embeddings_ad <- embeddings %>%
  group_by(.data[[id_var]]) %>%
  summarise(across(all_of(emb_cols), ~ mean(.x, na.rm = TRUE)), .groups = "drop") %>%
  semi_join(model_df %>% select(all_of(id_var)) %>% distinct(), by = id_var)

keep_emb_cols <- embeddings_ad %>%
  summarise(across(all_of(emb_cols), ~ sd(.x, na.rm = TRUE))) %>%
  pivot_longer(everything(), names_to = "term", values_to = "sd") %>%
  filter(!is.na(sd) & sd > 0) %>%
  pull(term)

pca_media <- prcomp(
  embeddings_ad %>% select(all_of(keep_emb_cols)),
  center = TRUE,
  scale. = TRUE
)

explained_var <- (pca_media$sdev^2) / sum(pca_media$sdev^2)
cum_explained_var <- cumsum(explained_var)
K <- which(cum_explained_var >= 0.80)[1]

message("Retaining ", K, " PCs (", round(cum_explained_var[K] * 100, 1), "% variance explained)")

media_pcs <- as_tibble(pca_media$x[, seq_len(K), drop = FALSE]) %>%
  setNames(str_c("media_pc_", seq_len(K))) %>%
  mutate(!!id_var := embeddings_ad[[id_var]])

model_df_media <- model_df %>%
  left_join(media_pcs, by = id_var) %>%
  mutate(
    has_media_embedding = as.integer(!is.na(media_pc_1)),
    across(starts_with("media_pc_"), ~ tidyr::replace_na(.x, 0))
  )

media_covariates <- c(
  "has_media_embedding",
  names(model_df_media %>% select(starts_with("media_pc_")))
)

# Covariate blocks for the paper and Supplement B.5
covariates_base <- ad_vars
covariates_age <- c(ad_vars, targeting)
covariates_media_only <- c(ad_vars, media_covariates)
covariates_media <- c(ad_vars, targeting, media_covariates)
```

# Main regression analysis (paper Figures 2, 3, and 5)

```{r}
# Main dependent variable in the paper
dep_var <- "excess_male_audience"

# Populist model with age-targeting and media controls
formula_populist_media <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media, collapse = " + "), " + country"
))

lm_populist_media <- lm(formula_populist_media, data = model_df_media)

inference_populist_media <- coeftest(
  lm_populist_media,
  vcov. = vcovCL(lm_populist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

coef_populist_media <- extract_coef_inference(inference_populist_media)
coef_populist_media %>% filter(term == "populistPopulist")

# Extremism model with the same controls
formula_extremist_media <- as.formula(str_c(
  dep_var, " ~ extremist + ", paste(covariates_media, collapse = " + "), " + country"
))

lm_extremist_media <- lm(formula_extremist_media, data = model_df_media)

inference_extremist_media <- coeftest(
  lm_extremist_media,
  .vcov = vcovCL(lm_extremist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

coef_extremist_media <- extract_coef_inference(inference_extremist_media)
coef_extremist_media %>% filter(str_detect(term, "extremist"))
```

```{r}
covariates_media
```


## Figure 2: Coefficient plot for selected populist-model coefficients

```{r}
coef_df_fig2 <- broom::tidy(inference_populist_media, conf.int = TRUE, conf.level = 0.95)

plot_data_fig2 <- coef_df_fig2 %>%
  filter(term %in% c(
    "populistPopulist",
    "platformFacebook",
    "platformInstagram",
    "party_ad",
    "sentimentPositive",
    "sentimentNegative"
  )) %>%
  mutate(
    clean_term = case_when(
      term == "populistPopulist" ~ "Populist",
      term == "platformFacebook" ~ "Facebook",
      term == "platformInstagram" ~ "Instagram",
      term == "party_ad" ~ "Party Ad",
      term == "sentimentPositive" ~ "Positive Sentiment",
      term == "sentimentNegative" ~ "Negative Sentiment"
    ),
    clean_term = factor(
      clean_term,
      levels = rev(c("Populist", "Facebook", "Instagram", "Party Ad", "Positive Sentiment", "Negative Sentiment"))
    )
  )

table1_coef_plot <- ggplot(plot_data_fig2, aes(x = estimate, y = clean_term)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(
    aes(xmin = conf.low, xmax = conf.high),
    color = "darkblue",
    fill = "darkblue",
    shape = 21,
    size = 0.8,
    linewidth = 1
  ) +
  labs(
    x = "Effect on Excess Share of Male Audience",
    y = NULL
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 14),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(color = "black", size = 12),
    axis.text.x = element_text(color = "black", size = 12)
  )

print(table1_coef_plot)

ggsave(
  filename = file.path(path_figures, "table1_coef_plot.pdf"),
  plot = table1_coef_plot,
  width = 18,
  height = 10,
  units = "cm"
)
```

## Figure 3: Marginal effect of populism on excess male share

```{r}
gge_populist <- predict_response(
  lm_populist_media,
  terms = "populist",
  vcov_fun = vcovCL(lm_populist_media, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

plot_effect_populist <- ggplot(gge_populist, aes(x = x, y = predicted)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = x), width = 0.2, linewidth = 1) +
  geom_point(aes(color = x), size = 3) +
  scale_color_manual(values = populist_colors) +
  xlab("") +
  ylab("Predicted excess male share") +
  theme(legend.position = "none")

plot_effect_populist

ggsave(
  filename = str_c(path_figures, "plot_effect_populist.pdf"),
  plot = plot_effect_populist,
  width = 10,
  height = 10,
  units = "cm"
)
```

# Figure 4: The role of political extremism

## Figure 4a: Female and male audience shares by country and ideological bloc

```{r}
df_extremist_gender <- model_df %>%
  filter(
    !is.na(country),
    !is.na(extremist),
    !is.na(actual_gender_distribution_unique_views_female),
    !is.na(actual_gender_distribution_unique_views_male)
  ) %>%
  mutate(
    extremist = factor(extremist, levels = c("Center", "Farleft", "Farright"))
  ) %>%
  group_by(country, extremist) %>%
  summarize(
    Female = mean(actual_gender_distribution_unique_views_female, na.rm = TRUE),
    Male = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = c(Female, Male),
    names_to = "gender",
    values_to = "share"
  ) %>%
  mutate(
    gender = factor(gender, levels = c("Female", "Male")),
    country = factor(country, levels = sort(unique(country), decreasing = TRUE))
  ) %>%
  complete(
    country,
    extremist = factor(c("Center", "Farleft", "Farright"), levels = c("Center", "Farleft", "Farright")),
    gender = factor(c("Female", "Male"), levels = c("Female", "Male")),
    fill = list(share = NA_real_)
  )

country_levels <- levels(df_extremist_gender$country)
country_gap <- 3.1
bar_offset <- 0.8
bar_width <- 0.75

df_extremist_gender <- df_extremist_gender %>%
  mutate(
    country_id = as.numeric(country) * country_gap,
    extremist_offset = case_when(
      extremist == "Center" ~ -bar_offset,
      extremist == "Farleft" ~ 0,
      extremist == "Farright" ~ bar_offset
    ),
    y_pos = country_id + extremist_offset
  )

extremist_colors_bar <- c(
  "Center" = "grey",
  "Farleft" = "#C44E7F",
  "Farright" = "#2B6CB0"
)

plot_extremist_gender_bar <- ggplot(
  df_extremist_gender,
  aes(
    x = share,
    y = y_pos,
    fill = extremist
  )
) +
  geom_col(
    width = bar_width,
    orientation = "y",
    na.rm = TRUE
  ) +
  facet_wrap(~ gender, nrow = 1) +
  scale_fill_manual(values = extremist_colors_bar, drop = FALSE) +
  scale_x_continuous(
    limits = c(0, 0.8),
    breaks = seq(0, 0.8, by = 0.2),
    labels = scales::number_format(accuracy = 0.1)
  ) +
  scale_y_continuous(
    breaks = seq_along(country_levels) * country_gap,
    labels = country_levels,
    expand = expansion(mult = c(0.01, 0.01))
  ) +
  labs(
    x = "Share of unique views by gender",
    y = NULL,
    fill = NULL
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(fill = "grey80", color = "grey40"),
    strip.text = element_text(size = 9),
    axis.text.y = element_text(size = 9),
    axis.text.x = element_text(size = 9),
    axis.title.x = element_text(size = 9),
    legend.text = element_text(size = 9),
    legend.key.size = unit(0.45, "cm")
  )

plot_extremist_gender_bar

ggsave(
  filename = file.path(path_figures, "bar_share_views_by_gender_extremist.pdf"),
  plot = plot_extremist_gender_bar,
  width = 8,
  height = 8,
  device = cairo_pdf
)
```

## Figure 4b: Excess male share maps by ideological bloc

```{r}
fig4b_df <- model_df %>%
  group_by(country, extremist) %>%
  summarize(
    excess_male_audience = mean(excess_male_audience, na.rm = TRUE),
    actual_gender_distribution_unique_views_male = mean(actual_gender_distribution_unique_views_male, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  right_join(eu, by = c("country" = "ISO_A2_EH")) %>%
  mutate(extremist = fct_relevel(extremist, "Farleft", "Center", "Farright")) %>%
  drop_na(extremist) %>%
  st_as_sf()

map_extremist_excess_male <- map_base +
  geom_sf(data = fig4b_df, aes(geometry = geometry, fill = excess_male_audience), color = "white", size = 0.1) +
  coord_sf(crs = lambert_crs, xlim = xlim_europe, ylim = ylim_europe) +
  scale_fill_gradient2(
    low = "darkred",
    mid = "white",
    high = "darkblue",
    midpoint = 0,
    limits = c(-0.2, 0.6),
    breaks = seq(-0.2, 0.6, 0.2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  facet_wrap(~ extremist, nrow = 1, ncol = 3) +
  guides(
    fill = guide_colorbar(barwidth = unit(10, "cm"), barheight = unit(0.5, "cm"), order = 1)
  )

map_extremist_excess_male

ggsave(
  filename = str_c(path_figures, "map_excess_views_male_extremist_new.pdf"),
  plot = map_extremist_excess_male,
  width = 20,
  height = 10,
  units = "cm"
)
```

## Figure 5: Extremism coefficient plot

```{r}
df_plot_extremist <- coef_extremist_media %>%
  filter(str_detect(term, "extremist")) %>%
  mutate(term = str_remove(term, "extremist"))

coeff_plot_extremist <- ggplot(
  data = df_plot_extremist,
  mapping = aes(x = term, y = estimate, fill = term, color = term, shape = term)
) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_pointrange(
    aes(ymin = conf.low.99, ymax = conf.high.99, fill = term, color = term),
    position = position_dodge(width = 0.6),
    linewidth = 0.6,
    size = 0.5
  ) +
  geom_pointrange(
    aes(ymin = conf.low.95, ymax = conf.high.95, fill = term, color = term),
    position = position_dodge(width = 0.6),
    linewidth = 1.2,
    size = 0.5
  ) +
  coord_flip() +
  labs(x = "", y = "") +
  scale_fill_manual(values = extremist_colors[c(1, 3)]) +
  scale_color_manual(values = extremist_colors[c(1, 3)]) +
  scale_shape_manual(values = c(21, 23)) +
  theme(
    legend.position = "none",
    panel.grid.minor = element_blank(),
    text = element_text(size = 24)
  ) +
  ylab("Coefficient")

coeff_plot_extremist

ggsave(
  filename = str_c(path_figures, "coeff_plot_extremist_cov_.pdf"),
  plot = coeff_plot_extremist,
  width = 10,
  height = 5,
  units = "cm"
)
```

# Supplement B: Robustness checks

## B.1 Alternative dependent variable (male share instead of excess male share)

```{r}
# Alternative dependent variable: share of unique views by male users
formula_extremist_dep <- as.formula(str_c(
  "actual_gender_distribution_unique_views_male ~ extremist + ",
  paste(covariates_media, collapse = " + "),
  " + country"
))

lm_extremist_dep <- lm(formula = formula_extremist_dep, data = model_df_media)
inferece_extremist_dep <- coeftest(
  lm_extremist_dep,
  vcov. = vcovCL(lm_extremist_dep, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)
coef_extremist_dep <- extract_coef_inference(inferece_extremist_dep)
coef_extremist_dep %>% filter(str_detect(term, "extremist"))

formula_populist_dep <- as.formula(str_c(
  "actual_gender_distribution_unique_views_male ~ populist + ",
  paste(covariates_media, collapse = " + "),
  " + country"
))

lm_populist_dep <- lm(formula = formula_populist_dep, data = model_df_media)
inferece_populist_dep <- coeftest(
  lm_populist_dep,
  vcov. = vcovCL(lm_populist_dep, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)
coef_populist_dep <- extract_coef_inference(inferece_populist_dep)
coef_populist_dep %>% filter(term == "populistPopulist")
```

## B.2 Alternative model specification (country-level male share controls, no country FE)

```{r}
formula_extremist_male <- as.formula(str_c(
  "excess_male_audience ~ extremist + ",
  paste(c(covariates_media, male_share_country), collapse = " + ")
))

lm_extremist_male <- lm(formula = formula_extremist_male, data = model_df_media)
inference_extremist_male <- coeftest(
  lm_extremist_male,
  vcov. = vcovCL(lm_extremist_male, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)
coef_extremist_male <- extract_coef_inference(inference_extremist_male)
coef_extremist_male %>% filter(str_detect(term, "extremist"))

formula_populist_male <- as.formula(str_c(
  "excess_male_audience ~ populist + ",
  paste(c(covariates_media, male_share_country), collapse = " + ")
))

lm_populist_male <- lm(formula = formula_populist_male, data = model_df_media)
inference_populist_male <- coeftest(
  lm_populist_male,
  vcov. = vcovCL(lm_populist_male, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)
coef_populist_male <- extract_coef_inference(inference_populist_male)
coef_populist_male %>% filter(term == "populistPopulist")
```

## B.3 Data sample restrictions

```{r}
election_date <- as.Date("2024-06-09")

model_df_2_months <- model_df_media %>%
  filter(ad_creation_time >= (election_date - months(2)))

lm_populist_2m <- lm(formula_populist_media, data = model_df_2_months)
inference_populist_2m <- coeftest(
  lm_populist_2m,
  vcov. = vcovCL(lm_populist_2m, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)
coef_populist_2m <- extract_coef_inference(inference_populist_2m)
coef_populist_2m %>% filter(term == "populistPopulist")

model_df_1_month <- model_df_media %>%
  filter(ad_creation_time >= (election_date - months(1)))

lm_populist_1m <- lm(formula_populist_media, data = model_df_1_month)
inference_populist_1m <- coeftest(
  lm_populist_1m,
  vcov. = vcovCL(lm_populist_1m, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)
coef_populist_1m <- extract_coef_inference(inference_populist_1m)
coef_populist_1m %>% filter(term == "populistPopulist")
```

## B.4 Modeling approaches

```{r}
# Propensity score matching for populist vs. non-populist ads
psm_populist <- perform_psm(
  data = model_df_media,
  balancing_vars = c(covariates_media, "country"),
  treatment_var = "populist",
  outcome_var = "actual_gender_distribution_unique_views_male"
)

print(psm_populist$balancing_tab)
summary(psm_populist$lm_model_adj)
print(psm_populist$ATE)

# Mixed-effects model with random intercepts for country
formula_populist_media_random <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media, collapse = " + "), " + (1 | country)"
))

lm_populist_media_random <- lmer(formula_populist_media_random, data = model_df_media, REML = FALSE)
summary(lm_populist_media_random)
```

## B.5 Sensitivity to covariate selection

```{r}
formula_base <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_base, collapse = " + "), " + country"
))

formula_age <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_age, collapse = " + "), " + country"
))

formula_media <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media_only, collapse = " + "), " + country"
))

formula_full <- as.formula(str_c(
  dep_var, " ~ populist + ", paste(covariates_media, collapse = " + "), " + country"
))

lm_base <- lm(formula_base, data = model_df_media)
lm_age <- lm(formula_age, data = model_df_media)
lm_media <- lm(formula_media, data = model_df_media)
lm_full <- lm(formula_full, data = model_df_media)

extract_populist_coef <- function(model, model_name) {
  inference <- coeftest(model, vcov. = vcovCL(model, cluster = ~ national_party, type = "HC1", cadjust = TRUE))
  coef_df <- tidy(inference, conf.int = TRUE, conf.level = 0.95)

  coef_df %>%
    filter(term == "populistPopulist") %>%
    mutate(model_spec = model_name)
}

ablation_results <- bind_rows(
  extract_populist_coef(lm_base, "1. Base Controls Only"),
  extract_populist_coef(lm_media, "2. Base + Media (No Age)"),
  extract_populist_coef(lm_age, "3. Base + Age (No Media)"),
  extract_populist_coef(lm_full, "4. Full Model (Base + Age + Media)")
)

print(ablation_results %>% select(model_spec, estimate, std.error, p.value, conf.low, conf.high))

ablation_plot <- ggplot(ablation_results, aes(x = estimate, y = forcats::fct_rev(model_spec))) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_pointrange(
    aes(xmin = conf.low, xmax = conf.high),
    color = "darkred",
    fill = "darkred",
    shape = 21,
    size = 1,
    linewidth = 1.2
  ) +
  labs(
    title = "Covariate Ablation: Effect of Populism on Male Audience Share",
    subtitle = "Comparing model specifications with and without age/media controls",
    x = "Estimated Effect on Excess Male Share",
    y = NULL
  ) +
  theme_bw() +
  theme(
    text = element_text(size = 14),
    axis.text.y = element_text(color = "black", size = 12, face = "bold")
  )

print(ablation_plot)
```

# Supplement C: Interaction between populism and political extremism

```{r}
formula_interaction <- as.formula(
  str_c(
    "excess_male_audience ~ populist * extremist + ",
    paste(covariates_media, collapse = " + "),
    " + country"
  )
)

lm_interaction <- lm(formula_interaction, data = model_df_media)

inference_interaction <- coeftest(
  lm_interaction,
  vcov. = vcovCL(lm_interaction, cluster = ~ national_party, type = "HC1", cadjust = TRUE)
)

coef_interaction_df <- tidy(inference_interaction, conf.int = TRUE, conf.level = 0.95)

coef_interaction_df %>%
  filter(grepl("populist|extremist", term)) %>%
  select(term, estimate, std.error, p.value, conf.low, conf.high)
```

# Multicollinearity diagnostic reported in the paper

```{r}
library(car)

calculate_vif_controls <- function(data,
                                   controls = covariates_media,
                                   include_country = TRUE) {
  rhs_vars <- controls

  if (include_country) {
    rhs_vars <- c(rhs_vars, "country")
  }

  vif_formula <- as.formula(
    str_c("actual_gender_distribution_unique_views_male ~ ", paste(rhs_vars, collapse = " + "))
  )

  vif_model <- lm(
    formula = vif_formula,
    data = data
  )

  vif_values <- car::vif(vif_model)

  if (is.matrix(vif_values)) {
    vif_df <- as.data.frame(vif_values) %>%
      rownames_to_column("term") %>%
      mutate(
        VIF_adjusted = GVIF^(1 / (2 * Df))
      ) %>%
      arrange(desc(VIF_adjusted))
  } else {
    vif_df <- tibble(
      term = names(vif_values),
      VIF = as.numeric(vif_values)
    ) %>%
      arrange(desc(VIF))
  }

  return(vif_df)
}

vif_controls <- calculate_vif_controls(
  data = model_df_media,
  controls = covariates_media,
  include_country = TRUE
)

vif_controls
```
